\documentclass[10pt, draft]{memoir}  
\usepackage{pifont}% http://ctan.org/pkg/pifont
\usepackage{charter}
\clubpenalty=10000
\widowpenalty=10000
\raggedbottom
\setstocksize{6.87in}{4.25in}
\settrimmedsize{6.87in}{4.25in}{*}
\isopage[12]
\checkandfixthelayout
\setlength{\emergencystretch}{2em}

\renewcommand{\pfbreakdisplay}{\bigskip \ding{166} \bigskip}
\newcommand{\secbreak}{\fancybreak{\pfbreakdisplay}}

\author{Daniel Darabos}

\date{2014}

\title{The Tree Far Away}

\begin{document}

\begin{titlingpage}
  \centering
  \vspace*{0.2\textheight}
  {\Huge \thetitle}\\[\baselineskip]
  {\large\itshape by \theauthor}\\[\baselineskip]
  \vfill
  {\itshape Written in 2012. \par
  Translated in 2014 \par from Hungarian to English.}
  \vspace*{0.1\textheight}
\end{titlingpage}

\par

Philip lived with his parents in a small house, which his parents had built together. The house was at the very end of a young leaf. The tip of the leaf moves the most when the wind blows, so her mother asked Philip every day to be careful. But on quiet evenings they all sat together at the edge of the leaf and dipped their feet into the endless abyss.

Thousands of leaves stretched out below them.

``Is every leaf like ours?'' Philip asked his father.

``On this twig, yes. But on the branch beneath us the fairies speak a foreign language. Above us they knit their houses on the bottom of the leaves because it is cold and the surface is more slippery. Each branch is different. There are places where fairies have never been.”

\secbreak

Philip became an explorer the very next day. He packed a dozen pollens, two folded fruitfly wings, and a blank travel diary and set off toward the stalk of the leaf.

The leaf where Philip lived was called Dewington. At every sunrise beads of dew grew on the roofs of the houses. When they grew as large as a pollen, they tumbled into the gutters. There they merged into spheres the size of a fairy's head and bounced off onto the veins of the leaf. The veins were the road network of Dewington, and every morning hundreds of dew spheres rolled across it. The kids played ball with them while the adults got annoyed whenever they knocked down a bench or a pot. By the time the sun had wholly risen above the horizon, the water droplets all flocked to the center of the leaf and merged into a giant sphere. The sphere sparkled in the light of the new day and all the inhabitants of the leaf made a stop at Dewington's main square in time to draw from the fresh dew water.

Philip too was headed for the main square. The chitin shop was just opening up as he reached the corner of the main street. He took a longing look at the wares. Among the shiny blades, thin needles, and plates in the window today there was an armor fashioned of radiant scales. This would just be the thing if he went hunting, Philip thought, but the hard suit would just constrain him as an explorer.

``Stop it!'' someone shouted from the right. As soon as Philip turned in the direction of the desperate voice, a dewball as big as a loaf of bread hit him in the face. He grabbed after the bounding drop but lost his balance and fell over onto the leaf.

Mary ran past, helped him up, and they chased after the drop of water together.

``Babouche is in the drop!'' Mary cried and threw herself upon the drop. She reached it but could not grab it from both sides, and the ball bounced from her hands. Philip too saw why they were after the drop now. Mary's paramecium was trapped in the ball of water. Parameciums are good swimmers, but if the small drop were to merge into the large one in the main square, Babouche would have to spend the rest of the day there.

The drop glided smoothly over the vein of the main street. Philip was a good runner and able to keep up with it, but he knew it would not be easy to stop the ball. There is nothing more slippery than the surface of water droplets. If they could not squeeze it in somewhere, they would never pull Babouche out of it. ``We have to get it onto the Stain!'' Philip shouted and shoved the drop into an alley.

The ambience here was nothing like on the main street. There were no inviting shop windows, no fresh scents drifted from restaurants, and the drop on the main square towering above the houses did not fill this street with its radiance. The murmur of life faded away behind them. As they chased the drop of dew through the passage they could soon smell the Stain ahead.

They ran past the last houses and found themselves in an endless brown desert. The withered leaf creaked and crackled loudly beneath their feet, but they did not want to lose Babouche now. The drop began to slowly shrink. The dry, dead surface gradually soaked up the moisture.

A dried flake collapsed under Mary's foot. She fell and more flakes broke under her, outlining her fallen shape. Philip turned back and took an anxious step toward Mary.

``Run on! Babouche is headed for the middle of the Stain!'' Mary said.

``We cannot run on. The leaf is entirely dead here. We have to be very cautious,'' Philip said and helped her up. They pushed on more carefully now. They still saw Babouche and also that the drop was almost completely gone. Once the dew did not cover him, Babouche tumbled to a stop. Still dizzy, he righted himself and sniffed around. He thoroughly shook his hair and nodded towards Mary.

``Do not move!'' a voice boomed from the distance. The two little fairies and the paramecium looked anxiously to the center of the Stain. From the distance a caterpillar's head stared back at them.

\secbreak

Every child knew the story of the Stain. Months before, Balthazar, the caterpillar, attacked Dewington. Knocking over houses on his way, he barged into the main square. The fairy warriors opposed him, but his hard skull protected him. The caterpillar headed from the main square to the most beautiful part of the city. He waded through well-kept parks, pierced the cellulose shop windows, and swallowed barrels full of nectar. He tore through the silk walls of the royal palace and dragged his soft body towards the treasury.

The palace staff panicked and fled, but George, King of Dewington, received Balthazar in the throne room.

``This leaf belongs to the fairies. If you would like to leave alive, turn around now and go back to whence you came,'' George said and lifted the royal sword off the wall. This weapon was forged against the larger inhabitants of the tree. Only the strongest of the fairies were able to wield it. The shiny blade was many times George's height. The tip almost reached the ceiling of the palace.

``I will be leaving,'' the caterpillar hissed, ``once I have fed, pupated and grown wings!''

He swung his head and snapped his mandibles toward George. The king raised his sword in front of him to block the attack. The chitin clashed against the metal, and sparks poured onto the floor of the palace. The strength of the caterpillar threw George towards the end of the hall, but he managed to grab a column and change his direction. He flanked Balthazar, cut down with the blade and severed the head of the caterpillar.

George sidestepped the aimlessly twisting body and looked into the eyes of the huge head. The rage of the short battle still burned in his veins. He was not only angry at Balthazar for what the caterpillar has destroyed, but also for what George had to destroy because of him. The dying caterpillar will never become a butterfly. At this thought the king was consumed with guilt. The hilt of the sword slipped from his sweaty palms and banged on the floor of the palace.

As in all fairy homes, the floor of the palace was the leaf itself. Industrious fairies had sewn patterns into the thin layer of wax that covered the plant cells in the throne room. The heavy sword lay across the path of an ant caravan embroidered in golden thread. George's eyes followed the line of ants to Balthazar.

``No!'' George shouted. But even if the caterpillar had a drop of goodwill in him, he had not enough life left to listen to the king. His mandibles dug into the decorated leaf and a bitter venom seeped into the wound. The leaf turned black around the wound and the dark stain started to grow.

George stumbled back. The black venom filled the floor of the palace right in front of his eyes. He watched helplessly through a window as the streets around the palace were painted black one by one. He felt as though the caterpillar had poisoned his heart and the bitterness had spread through his body. The streets turned black, the buildings turned black and the sky did too.

\secbreak

Many days had passed since then. The one-time king now served hot tea to his guests. Mary and Philip sipped quietly from the steaming cups and looked at the wasteland through a round window. George's voice had stopped them from chasing after Babouche onto a dangerously fragile region. Weeks before, the palace stood here, and here fought Balthazar and George. The caterpillar injected his poison into the leaf here, and those who fled from him never returned to the blackened streets. Thankfully, there was not enough of the poison to kill the entire leaf. But within the Stain the leaf withered and the houses collapsed.

The caterpillar's body had dried up and drifted away. The head, however, still clung to the dead leaf. The wind took the palace as well, but the king could not leave the Stain behind. He took up residence inside Balthazar's dried head, and they looked out through his eyes over the wasteland.

``How could the Stain be healed?'' the ever-curious Philip asked.

``No such magic, unfortunately,'' the old king replied. ``But the spring will heal all.''

``We are big kids now,'' Mary interjected. ``We know the spring is not real. It is only our parents who decorate the house in the morning.''

``Oh, you have really grown up! Philip may indeed be swinging the royal sword come tomorrow! But I am sure you have noticed that the days are shorter now than when you were small. You can play less and have to learn more.''

The two youngsters nodded ruefully.

``With time the days run out, the leaves wither, and the fairies hide. It will be your duty to emerge when the spring comes and rebuild everything. Your leaf will grow as you build your town, and you will play spring for your little fairies.”

Philip and Mary listened to George's prediction. The adults always talked about the seasons. But the kids could not yet decide whether they really existed or not.

They accepted another cup and listened to a story about how George bought the leaf of Dewington from the ants for the price of seven aphids. They said goodbye then, and the king taught them the safe path through the cracked surface of the Stain.

``Thank you for your help!'' Mary said on their way back. ``Thanks to us Babouche is not stuck inside the drop!''

``I am glad to have helped.''

``If you want to help some more, let us bring a little water for my fungus.''

\secbreak

The main square was alive with a colorful crowd of fairies. Most came to fetch water from the huge drop of dew. But many people stopped to chat, vendors offered their wares, and old fairies bathed in the light of the rising Sun where the big lens focused it into a spot.

Mary formed a capillary from her hands as good as any adult. She touched it to the surface of the drop, and Philip hurried to pick the outflow of dew dumplings into his bag. One droplet tried to roll away, but Babouche sipped it up.

Mary was growing a tiny fungus in her room. It was a present from her aunt, and she wholeheartedly believed it would turn sweet as honey with just a little more tending. Only someone who never tasted it could have believed that, Philip thought. He had tried a little tendril when they came over for lunch. It was terribly tough and bitter. Since then he avoided the oddly shaped germ. He excused himself on account of his important work as an explorer and said farewell to her.

\secbreak

Philip came to the stem of the leaf. He looked back one last time at the drop shining among the fairy buildings and knew this was it. He was about to become an explorer. He jumped on the stalk and slid into the unknown on his buttocks. He remembered her grandmother's stories about the ground. The old fairy had told him that even the ants were afraid to climb down that far because there were monsters there that could swallow a whole ant. Fortunately, these creatures were too large to walk upon the leaves, so the fairies had nothing to fear. But what if a little fairy left the leaves?

The leaf grew from a young twig. The stalk had big green bumps at its base to keep it firm. These bumps cushioned Philip's arrival. Although he had no choice in the matter, he decided he was better off with three small thumps than a single big one. Fearing his grandmother's monsters, he slid into a fairy-sized cranny and peeked out from there. He saw monsters neither to the left nor to the right.

The twig was about the width of a whole block of buildings and stretched to the horizon in both directions. Its surface was much rougher than the leaf. A fairy could always find a niche here that would serve as emergency shelter. This put Philip at ease as he climbed out of the narrow crack. He circled the stem and thought about how he would climb back up at the end of the expedition. The stem was covered in a strong wax. Pants slipped well on it, but small fairy fingers would pierce it and find a good grip.

He could see which way the stalk leaned, and Philip walked off in that direction. He looked up curiously. He spent his entire life on its other side, but had never before seen the bottom of the leaf. He could see the veins, and the brown circle of the Stain was clear as well. Philip unwrapped his travel diary and made a drawing of what he saw. He had hardly seen a prettier map of Dewington!

After a bit of a walk he glimpsed a pair of antennae bobbing above the curvature of the branch. He had nothing to fear from insects on Dewington. But Philip did not know what to expect in the wilderness outside of the leaf. He watched the approaching antennae from a crevice. The antennae undulated on the great black head of an ant and a body followed behind. A bit later there was another ant head and another ant body. Three ants were approaching Philip.

The ants were regular guests in Dewington, although the fairies did not always understand them. Shiny chitin covered their huge bodies, even stronger perhaps than the royal sword. The leaf trembled beneath their feet. Their mandibles could have carried all the houses of the main street at once. Yet they never caused trouble. Each day an ant would come, walk around the leaf without a word, taste the dewdrop, and return to where he came from. Philip's parents said the ants are looking for garbage, and therefore everything must be kept clean. Mary had heard they were looking for bad kids. And yet, Philip was not taken when he misbehaved.

Philip felt that he had not been bad that day. In fact he had been good. He stood in front of the ants and awaited them with his hands on his hips. The ants seemed big from afar, but they just grew and grew as they approached. Philip could have hid behind one leg.

The ants did not notice Philip, or they were in a great hurry. The heads, thoraces, and abdomens the size of houses passed high over him. He spun around in surprise below. But no matter the waving and shouting, they did not stop for him.

``Wait! I am headed the same way! Let's go together!'' he shouted after them, but the ants did not wait. Philip ran after them and pounced on one of the huge legs. He held on tight, as the foot rose into the air. ``Wait, hold on! I am going to fall!'' he pleaded with the ant. But it was either deaf or did not speak the language of the fairies. Philip was a skilled climber of course, and with some difficulty managed to reach the ant's knees. ``Why such a hurry? Is the winter chasing after you?''

Philip walked over the ant's thigh, cut across the jungle of hair on the thorax, and found his way to the ant's head. ``Here we go,'' he said as he settled between two hairs perfect for holding onto. ``We can go on now.''

``I am Philip, the explorer. You must have been to many places, Mister Ant. Have you been to the top of the tree? It must be quite the view. Maybe you can see beyond the end of the longest branch. Although I do not know how well you ants see. Perhaps you do not even see me? You do not hear me. Not even when I sing?''


\begin{verse}
TODO: song
\end{verse}


At the end a low bass voice repeated the melody of the last line. The ant under Philip was humming it.

``Oh, so you can hear me! What is your name? Where are we going? Why did you not say anything?''

``Yes, I can hear you, Philip. My name is Tony. We are patrolling the boundaries of the empire. If someone intruded, something broke, or we found something of value, we would report it to the hive. We have important work to do. We do not have time to talk and sing.”

``I see,'' Philip said. ``Can I ask you something? How big is the Empire? Is the whole tree your empire?''

``No,'' Tony replied. ``From where we are it extends six branches down and four branches up. The tree has no end, but an empire needs a border. Otherwise it could not be defended.''

``But each branch has an end and the trunk is also becoming thinner. It ends at the top and there is nothing but blue sky above it. Had it no end, the infinite number of leaves would block out the sky. Sunlight would never reach us and we would live in eternal darkness,'' Philip explained. ``Did they not teach you in school?''

``Ants do not go to school. We know all as soon as we hatch. We do not need to learn.''

``I wish I could be an ant! But what if someone invents something new? Will you also know that? Or will only those that hatch after know it?''

``A good ant does not invent anything. We take the bad ants to the border of the empire and never let them return.''

Philip did not like that. The best thing about exploration was learning new things. But he kept quiet rather than argue with his travel companions. Especially given that Tony was also his swift mount. He leaned back comfortably instead and enjoyed the sunlight breaking through the canopy. What could the outcast ant inventors be up to? Surely they are sad that they cannot go home. But they can go explore. And if they invented something clever, they must fare even better than the ants of the empire. They may be building wonderful cities in remote leaves. Maybe they spin whole leaves into palaces and live in them at the very top of the tree.

\secbreak

Philip awoke to some nudging. The touch was similar to Babouche's, but hairless and hard. As he opened his eyes, four long black antennae were swaying overhead. He sat up and saw that he was still riding on Tony's head. But they were facing another ant, and its antennae had woken up Philip.

``Where are we? Why are we stopping? I fell asleep for a little while,'' the fairy said.

``We have reached the end of the patrol route. This is the border of the empire. We found everything to be in order and are going back to the hive,'' Tony said.

Philip was curious about the ant hive, but the ants did not invite him and he did not want to be pushy. Instead, he looked up to the top of the tree and took a deep breath. The trunk seemed to stretch into infinity, and what the ants said had worried Philip a little. But he was determined to climb to the top of the tree and prove that ants did not know everything.

Philip thanked the ants for carrying him that far and said goodbye. He also learned that the empire of woodpeckers lay above the empire of ants. It was extremely dangerous for insects, but Philip knew that birds were so unbelievably large that they could not see fairies. He was more afraid of the amoebae and other feral protists hiding in the rough of the bark.

The thick bark made the climb easier. Philip did not have to use his hands. It was just like going up a staircase. Moisture remained here and there in the dark corners of the bark; Philip carefully avoided these. Wild relatives of Babouche lived in the water droplets. They would have surely snapped at the fairy's ankles if he stepped on the water.

At the bottom of one deep shadow, however, something bright caught Philip's eye. It was neither the glint of water nor chitin. As Philip searched for handholds and flat surfaces on the way to the small cave, the brightness seemed to float in the air. Its shape and size was like a fairy's forearm. Its surface gleamed in the darkness of the cave as it rotated. Philip could not take his eyes off of it. Leaving behind his usual caution, he approached the curious object.

The tiny space under the bark was almost completely dark. From time to time the faces of the mysterious object reflected the brighter world behind Philip. He reached for it and saw the distorted image of his hand on the crystal surface. He took it and turned it around in his hand. How was it floating in the air? How can it be so shiny? Why such a strange shape? It could be better examined in the sun...

As Philip turned, he found himself facing a dark creature. A spider spawn, full of legs and eyes, blocked his way out of the cave. The adult spiders were even larger than ants, but the youngling facing Philip was shorter than a fairy.

``Thief,'' it hissed and approached Philip. ``You wanted to steal my treasure. But I have caught you red handed. And I have to prosecute you to the fullest extent of the law.''

The spider raised four legs menacingly and spread them wide. But Philip was not so easy to scare. He jumped on the spider, and they began to wrestle. The eight long legs gave no advantage to the spider in close combat. Philip's momentum upended it and the legs waved in the air in vain. Its mandibles snapped, but Philip’s hands pinned its cephalothorax to the ground. With yarn spun from its abdomen it tried to tie up the wildly attacking fairy, but had no luck. As the wrestlers got entangled in more and more threads the fight slowed down. Soon seven of the spider's legs were bound to Philip's right ankle in a knot of yarn. The end of the eighth leg was in Philip's grip. The spider looked up at the fairy with eight disheartened eyes.

``I was just kidding,'' it said. ``You can have the looking stone.''

``Thank you,'' Philip said, and he caught the crystal swinging from a thread. ``I am Philip, the explorer. What is your name?''

``Greg, the cunning,'' the spider spawn introduced itself proudly and shook Philip's hand with a foot. ``I am practicing laying traps. You are my biggest quarry so far.''

Philip did not want to discourage the little spider. He turned the conversation from the topic of the efficacy of the trap.

``What does the looking stone do? Come, let us go out to the sun and take a better look,'' Philip said and walked towards the exit of the cave with the spider still tied to his foot. Greg tried to contribute to the walking with its one free leg.

``The looking stone is a very tiny grain of sand. The curved surfaces distort what you see in a peculiar way. When you look through it, everything is yellow, upside down, and seems much closer than it really is,'' the tied spider spawn said. Philip raised the crystal to his eyes and looked around from the bark of the trunk. If he turned even a little, everything moved swiftly in the stone. But once he held it very carefully, the distant leaves seemed as if he were standing on them. Just more yellow. And upside down.

Philip could not have enough of it. He turned the looking stone from one leaf to the next. He watched distant fairies, ants, spiders and parameciums. Looking up, he found fairies which really lived at the bottom of a leaf. They plastered the houses to the leaf, had to build floors instead of roofs, and walked on yarns stretched between their homes. Following along the branch, Philip saw the toes of a giant bird and then the last leaves. And, beyond the branch, another branch. Another tree. Everything looked smaller there, and Philip could not tell how fairies lived their lives on other trees. But he could still spot larger animals there with the looking stone.

``Look, Greg! Spiders live over there too! Do you know them?'' he asked his new friend. But in place of the little spider there lay just a discarded pile of silk thread now. The spider spawn had escaped while Philip admired the looking stone. He could not find the spider in the cave nor in the surrounding area. He carefully wrapped the looking stone and put it in his backpack along with the thread from his ankle. He continued on his way up, hoping that Greg went the same way, and they would meet again.

\secbreak

Further up the easy climb through the fibers of the bark was interrupted by a great hole. The rind was missing in an area the size of a small leaf. A deep fissure opened into the body of the tree. Of course an explorer's job is to investigate these kinds of mysterious places, so the little fairy walked around the opening to find out more.

The gorge was deep, and Philip suspected the woodpecker. He knew the sound of pecking. He learned in school that is how woodpeckers find the tunnels that larvae build in the wood. The fairies were grateful to them for removing the pests of the tree and also for not eating leaves. But it was a different matter to hear about it and to stand alone in the great crater.

His suspicion was confirmed when he came upon the wide mouth of a tunnel. The tunnel opened to the left and to the right from the hole drilled by the woodpecker. Philip reached the opening on the right. It sloped upward while the opposite tunnel seemed to descend. Did the woodpecker catch the larva? Or did it scurry back into the tunnel and sneak away from the bird?

``Hello,'' Philip called into the cool gloom of the tunnel, but only the echo replied. He set out to explore the passage.

The slight initial slope gradually turned steeper. In the vertical spans Philip had to climb skillfully because the tunnel wall was much smoother than the bark. But he could also move faster because he did not have to find the path and avoid protists hiding in droplets.

As he got further from the hole made by the woodpecker, it turned darker and quieter. A steady breeze filled the shaft, which thankfully pulled Philip up and made it easier to progress. The little fairy knew it meant an exit was waiting at the end of the tunnel.

The darkness was not complete yet when the tunnel started getting brighter again. The weak light had a yellow tint, as if it had entered the tunnel through the looking stone. The light was growing stronger until Philip reached its source. The light of the sun filtered through the wall of the tunnel. Thin plates of wood lent it their yellowish color. At the center of the ring of light was a hole the size of a fairy. The draft left the tunnel through this hole.

A strange scene awaited little Philip in the yellow glow. An ant stood opposite the radiant gate. It stood not on six legs, like normal ants do, but on two, like a fairy does. The other two pairs of legs were clasped in front of its body, as if it were praying in the alcove of the tunnel. Peculiar designs covered the walls of the tiny shrine. The ant must have had carved the lines into the polished wood.

Philip sat down at the entrance of the shrine and watched the silent ant in awe. He could not figure out what the lines meant, and was eagerly hoping the ant would explain when it woke up. He got hungry from the long climb and unpacked two lovely balls of pollen to pass the time usefully. His hands also found the looking stone. Close up, however, the ant looked like an endless golden statue. Flipping the stone around pushed everything into the distance. The unwrapped pollen seemed unreachable. But Philip's hand also stretched like a spider's thread and fetched a remote morsel to his mouth.

\secbreak

Ants do not blink. Their eyes are covered with thin chitin. They do not need moisture. Philip did not know if the ant was watching or asleep. He had barely finished the first pollen when movement caught his eye. The ant spread its middle pair of legs, then the top pair, then froze into this new pose.

``Would you like some pollen?'' Philip asked and offered the second ball to the ant. ``Do you live here? Were you banished from the empire? What did you invent? These carvings are beautiful. Were they the reason?''

The ant did not respond but accepted the tiny snack with a slow movement. It brought the pollen leisurely to its mouth and ate it.

``Do you know any other exiles? What things have you invented? Will you teach me too?'' Philip saw a secret ant city built at the top of the tree in his mind's eye. This mythical place would have been the prize of his expedition. All he wanted to hear was the ant acknowledge its existence.

``I found the truth. The light. This is the shrine of radiance. The sun is the source of all life,'' the ant replied. ``The empire of the ants would be lost without the rays of the sun as well. And yet they cast me away. They did not want to build the temple of the sun. I have to do the work on my own.''

``I'm happy to help!'' Philip suggested.

``The sun is waiting for us at the top of the tree. But I cannot go any further. Please, take this song to the top of the tree.”


\begin{verse}
TODO: sun song
\end{verse}


Philip recorded the song in his diary and said goodbye to the ant.

\secbreak

Philip had to squint his eyes as he crossed the gate of the shrine. He was high up in the tree, much closer to the sun than Dewington. The pollen had filled him with satisfaction. So had the old ant speaking about the top of the tree. He rose towards his goal with light strides.

The merry walk ended abruptly when Philip slipped and fell on his back. As he got on his feet his fingers felt strange slimy forms. Everything around him was covered with yellow bacteria. They were teeming across the tree bark, spreading their slippery mucus over it. They surrounded Philip and nudged his shoes with their noses. Kicking the fingerlings out of his way he retreated to the dry area of the bark. Looking up, he saw that the germs covered most of the way up. They used the slippery mucus to extract nutrients from the bark. Philip did not feel a rash on his skin, so the mucus was not dangerous. On flat ground he would have carefully cut across the field of bacteria. But it was impossible to continue the difficult climb like this.

Philip looked for another route. Due to the curvature of the trunk he could not see how far the bacterium colony extended. But he saw a thick branch level with the ant's shrine. After climbing onto this branch he was better able to assess the situation. The bacteria did not infest the area by accident. Above them was the nesting hole of the woodpeckers and the slimy microbes lived off of their waste. He could not see how much of the other side of the trunk the unnavigable field covered. But Philip would rather not want to risk the trip. The yellow bacteria were harmless, but more dangerous varieties could also be living in the area.

Deep in thought he walked on along the branch. As he got further from the trunk he got a better picture of the layout of branches. If he could somehow get from one branch to another, he could keep his distance from the woodpeckers and continue his journey.

Philip stumbled again and fell forward this time. The sound of a string plucked filled the air. It still hummed when the fairy got back on his feet and started looking for the invisible obstacle that had tipped him over. He found it by the sound and the vibration. A clear yarn the thickness of a fairy's finger was fastened to the branch. The yarn rose into the air at an angle. No matter how Philip squinted he was unable to make out the other end of the fine strand. He hoped that it might be a way to a higher tree branch.

He extended the line of the string in his mind and tried to guess which branch the other end might be tied to. Halfway to the next branch, however, he spotted something on the imaginary line. A huge black spider seemed to float in the air. Its legs worked the fine yarn, and before Philip could tell whether the spider was coming or going it was already standing above him.

``Well, well, look what my web has caught,'' the spider droned as it towered above Philip. ``If it is not one crafty fairy!''

``Sorry, I missed the web. I am Philip,'' he started his introduction.

``The explorer. Yes, I know. Playmate of Gregory. I am his mom. Should I ask him if he wants to come down and play?''

``Thank you. But the truth is I would rather go up. Where does this thread lead? Can I get to the next branch this way?''

``Of course! You are very welcome to use our web free of charge. I can also offer you an inexpensive map if you need one,'' the spider said slyly.

Philip knew the story of John. The fairy knight went to fight an evil spider who exploited the inhabitants of the leaf. After a long journey he had found the web of the spider and began to climb. The spider saw the fearsome sword and fled to the other side of the web. John chased after it and deftly climbed the yarns of the net. But the spider always avoided him and the web become ever stickier under John. Only the spider knew which thread was sticky and which was safe.

In the story John cut off the web with his sword and chased the spider out of the tree. But Philip had no sword nor did he want to cut off the web.

``What would you ask in return for the map?'' he asked.

``Knowledge for knowledge'' the spider mom replied. ``Teach me how to knit a nice jacket like yours. I have a lot of yarn and would like to knit a winter coat for Gregory. But I do not know how to work the thread.''

So it came to pass that Philip taught the spider to knit.

\secbreak

Once the spider had learned enough, she started knitting a simple square cloth. She wove an intricate pattern from three alternating fibers. Line by line she revealed a map of the web to Philip. Seven long threads anchored the web to various branches. Radial fibers stretched between them, and a dense spiral of sticky threads covered them. A network of walkways allowed the spiders to get around without getting stuck.

The map of the secret walkways was very useful. But Philip's attention was drawn to something else. The spider had laced detailed pictograms at the seven anchor points. Philip recognize only some of them. A woodpecker was peeking out of a hole where he had met the spider. An aphid was grazing at another anchor at the same height. At the other end of the thread a fairy was smiling. To the left, a squirrel was chewing on something at the anchor of the web.

Philip's eyes gleamed as the spider knitted the map. He had not even dreamt of so many things to explore. A whole day would not be enough to uncover all these secrets. He had to decide which one of the threads to leave the web by first. The top of the tree was still the destination of the expedition, so he chose a yarn leading high up, to the smiling fairy.

Philip was no spider and one branch was far from the next. Greg accompanied him for a span, but the climb still felt endless. Gradually, however, he began to suspect where the thread led. It was not fastened to the bark of a branch as the anchor at the woodpeckers, but to the bottom of a leaf. And as he came closer, he saw it was not fastened at a single point. On approach the thread unwound into three fibers and ran to three different sites on the leaf. Philip chose the one closest to the tip of the leaf.

When he got close enough to see the fairy buildings, a busy city spread out ahead of him. As seen through the looking stone, the inhabitants built their homes on the bottom of the leaf. Garish floorings adorned the bottoms of the houses. Colorful, fenced terraces and the hanging bridges between them served as streets for the fairies of the city. Thin threads connected one porch to another across distances great and short, for sending messages and getting around. Philip also noted an interesting method of freight transport. From time to time big packages swung through the air from one end of the leaf to the other. Fearless fairies stood upon them and guided the shipments to their destinations by leaning against the thread.

The spider thread, on which Philip climbed, led inside a large building. The atrium around the silk connected three floors. On each floor planks reached out the thread to make getting on and off easier. As Philip stepped on the plank of the first floor, exhausted from the climb, he found himself right inside a busy warehouse. An army of strong fairies filled the floor. They carried large bales over their heads and directed the loading process through loud jabber.

``Where are the rest of the algae?'' someone called down from the second floor. ``Hey, little fairy! Go ask which storeroom they put the algae in! We've got to ship them to grand central.''

There was no such organized trade in Dewington, but Philip was used to conveying messages between adults. He ran among the stevedores and asked where they took the algae. They took them to storeroom three.

``They took them to storeroom three!'' Philip shouted upstairs.

``Why not to number two?!'' the fairy upstairs grumbled. ``All the same in the end. Let the cranksmen in the loft know they can get started. We cannot wait any longer.''

Philip did not understand much of this, but he grabbed the spider silk from the plank and climbed up. The end of the thread was not fastened to the surface of the leaf. It wound around a big reel, thickly covering the axle. A large wheel was attached to the axle and could be pulled by many fairies from both sides of the floor.

Philip let go of the thread and ran to the waiting workers across the plank to gave them the message. They sprang to action at once and eagerly started turning the big wheel. The spider silk stretched and twisted around the reel. Up close, it seemed as if they were pulling the web closer to themselves. But Philip realized that the web was not moving. As the thread shortened, the leaf itself swung into motion. With each turn of the wheel the entire leaf, the entire city bent a little.

He was impressed by the legion of workers and the stream of goods their hands unloaded. Philip helped out for a while in the silk docks. He got to know the local fairies and the history of the leaf in the short breaks between loading and unloading. They collaborated with Greg's family and had built a trading network along the silk threads. The spider family supplied them with plenty of silk and assisted in setting up the system of reels. In exchange, the fairies offered special delicacies, spices, news, and colored crystals to the spiders.

At the end of the shift the workers invited Philip to lunch. After a hearty meal they produced their greatest pride, the spider brandy. Philip had not heard of it in Dewington. Seeing his interest, the locals started on a detailed explanation. Those with eight legs and those with two enjoyed this distillate equally. The golden dewdrops condensed at dawn on the bottom of the leaf and of the fairy buildings. Teams of fairies collected the tiny droplets into large barrels using safety harnesses and agility worthy of spiders. Later the heady beads were tapped whenever the fairies gathered and danced together.

Their best kept secret was the origin of the golden droplets. The spirit rose to the leaf dissolved in warm air. The touch of the cool surface forced it into a liquid form. The air was warm from the light of the new sun and lifted off of a leaf on the branch below. Upon this leaf the fairies had put a herd of gentle aphids to pasture. The aphids produced honeydew, and the fairies fermented a part of it with the help of a fungus. The heat of the rising sun evaporated the spirits from the fermented droplets, and these spirits ended up in the barrels of the city.

Philip did not try it, but the fairies said it tasted like sunlight. After a sip the fairies would feel like they were basking in the summer sun. Their city was named after this beverage. Solperla, he learned from the locals, means ``pearls of the sun'' in some language.

The spirit round and yellow and could be ignited by a spark. It would give off light and heat then, and could burn a careless hand. A round black spot, not unlike the dry Stain of Dewington, marked the invention of fire in Solperla. The fairies had mastered the use of fire since then. At night a tiny flame always flickered below the city. The light helped travelers find their way home and drew many unwary insects into the spiders' web. The spiders would mistrust the dangerous beacon at first, but the rich harvest soon convinced them.

Philip said thanks for his lunch and for the interesting stories, and headed off to explore Solperla. He welcomed the change of pace after the flurry of the docks. He walked through the bridges of the city and looked down on the leaves below. He knew one of the leaves had to be Dewington. But even with the looking stone he found it impossible to find where he had set off on his journey in the morning.

\secbreak

Philip soon found himself playing tag with a flock of Solperlan children. The game took more skill than in Dewington. Even the smallest fairies knew all the bridges and all stray threads. They walked across silk fibers, swung on tufts hanging from terraces, and every time they seemed to dive into the deep, they always caught on to a ledge or overhanging fabric.

Philip could barely navigate the maze of suspension bridges so he often got to be ``it''. At one time he was chasing an older playmate. The boy gained distance through a series of unexpected shortcuts, but Philip did not give up the pursuit. They were heading for the stem of the leaf, and he knew that the labyrinth that was Solperla would come to an end there. The network of swinging bridges, terraces, and spider silk woven between them was running out ahead of the boys. Nowhere to run, Philip tagged him with a good lunge.

Of course the crowd of local children was right on their heels. As the fresh ``it'' turned around and started after them, they scattered screaming. Philip was left alone at the edge of Solperla. The wild pace of the chase still pounded in his ears. But his eyes turned to the stem of the leaf, and his heart settled down. If he wanted to get to the top of the tree and get back to Dewington before dinner, he could not spend any more time playing.

At this altitude the trunk was growing thinner and the horizontal branches were getting shorter. The bark was also younger and smoother. The tiny hands of a fairy could still find a hold, of course. The smoother and younger surface just meant that Philip did not have to worry about germs lurking in dark cavities. With each passing branch and twig the foliage above him grew thinner, and at last the trunk ran out. Two leaf stalks grew at the end, and Philip began to climb the one that led to a higher leaf.

He saw nothing of note from below, but Philip knew something exciting must wait for him on the other side. It was impossible that he would not find something special on the very highest leaf of the entire tree. Perhaps the magical city of outcast ants would be revealed? Or the sun itself lived up there in a glowing palace? In his court a bustle of fairies would walk around in strange dresses, important papers in their hands, and they would have no time for Philip?

When he came level with the leaf, he counted to three. Then, ready for anything, jumped on top.

\secbreak

The top leaf was more slanted than the rest, and Philip almost tumbled right back from it. He regained his balance, but found nothing exciting other than that. The immaculate green leaf was completely barren. Walking through the central vein he could have as well been walking down the main street of Dewington in the early spring, before the fairies had arrived.

It felt good to stretch out on the soft warm surface after the long climb. It felt good to cartwheel and roll down the main street. And it felt good to run around in circles. Half a circle down the slope, half a circle up the slope. It felt good to climb to the tip of the leaf too, where his father and mother would have awaited him, were this leaf Dewington. And at last it felt good to look at the whole wide world from the highest point of the tree.

He had seen distant leaves from the window of his own room. He knew the most remote ones grew from branches of a different tree. He knew that birds fly from one branch to another and can fly from tree to tree as well. But all that did not prepare him for the sight of the forest. Philip's tree stood in the side of a larger hill with great view of the rolling landscape. An infinite multitude of trees covered the hills. There were more trees in the forest than leaves on a tree. The tree is finite, but the forest seemed boundless.

And every tree was different. One was taller, the other lower. Some had berries, others had cones. Even their leaves were not the same. Philip looked in awe and tried to imagine what life might be like on the oddly shaped leaves. Some were round, while some had three or five tips. Many leaves were larger than Dewington. But many were less green than those on Philip's tree. The autumn seemed to have arrived already on other leaves. The rolling hills were shining yellow, red and brown, as if they had caught fire from the setting sun. The sun's disc shining through the clouds reminded Philip of the song of the old ant.


\begin{verse}
TODO: sun song
\end{verse}


The song teased the sun out from behind the clouds, and it flooded the hills with golden light. A lark flew up from a nearby tree and called its playmates with a sharp squeak. Some did join it in flight, and they danced in the sky. Some joined them in song. But all of a sudden they all vanished.

Philip lifted his hand to his eyes and looked between his fingers toward the distant hills. A second sun rose from behind the horizon. Its flickering light seemed to set fire to the colorful slopes. The dark clouds became shadows. The song of birds dwindled. Every creature in the forest was watching the awesome sight.

The blinding light rose slowly, and soon a deep rumble filled the landscape. Philip was watching the strange phenomenon lying down on the leaf. The rumbling sound grew louder and louder, and Philip was frightened to see that a wave was sweeping through the forest. The trees bowed in its way. Their yellowed leaves were cast high. Flocks of birds took flight in panic. The wave rolled out from the new sun through the landscape and relentlessly headed toward Philip.

Philip did not exactly know what was going on, but his instincts put an end to the placid observation. Without thinking he jumped up and ran. Away from the tip of the highest leaf, away from the path of the wave tearing everything up. He ran down the barren main street of the leaf, slid down the smooth stalk and held on to the unyielding bark of the trunk. And then the wave hit.

The whole tree shook from a dreadful thunder. The air was filled with whirling grains of sand. Entire leaves tumbled among them, and Philip could even see twigs torn off as a whole. A bird was escaping the bustle, but unpredictably writhing branches got in its way. Philip held on to small cracks on the bark with all his might and hoped to see his family again.

Sand grains the size of a fairy tore at the branch around him. A brown leaf covered him, and blotted out the glare for a moment, but then the wind carried it on and tried to take Philip along. Tiny droplets of mist peppered around him, and the landscape swung into motion as the trunk bent. Something grabbed Philip and they both tumbled into the void.

\secbreak

Fortunately, Philip had clung to the bark for the worst of the blast, so they fell straight down. They whooshed past a branch, then the next one generously extended a leaf in their way. Head over heels they landed on the surface in a heap. The world revolved around them while the trembling of the leaf slowly subsided.

Philip sat up, and an old blue fairy sat up against him.

``Oh, my, where may I be,'' said the blue-skinned lady. She straightened out her fine clothes and put a strand of hair back into the tangle on her head.

``Thank you for helping me land here, little fairy,'' she thanked Philip. ``That's strange weather, is not it? We'd better go look for your parents and make you a nice cup of tea. You have paled entirely, I see the blue has drained from your face.''

Philip felt his face in surprise. Indeed, it was not blue, but it was not usually blue.

``I am Philip, the explorer,'' he blurted out for lack of something better.

``Oh, such a very nice name. I am Raisy. Which leaf did you leave for your expedition, Philip? I think we have seen it all now and it is time for a rest.''

Philip agreed with this. As soon as the tree settled down, they started their journey towards Dewington.

Rasiy was as small as Philip, despite being older than even the adults. And she was very blue. The wind flew her off of a distant tree, and she said everyone was blue there. She knew a lot about the forest, and even knew that the new sun that rose so violently was called a rocket. Its grumble had faded by then, and when they spotted it in between the leaves, its brilliant flame had shrunk to a pinpoint.

``How are you going to go home, Raisy?'' Philip asked. ``Maybe you could jump from a very long branch to a neighboring tree, but the journey would take days.”

``Weeks,'' Raisy corrected him. ``The autumn is knocking on our doors. We cannot go on such long journeys now. There is nothing to eat on the withered leaves, and they will all turn brown before I would get home. I will have to move in with your family, Philip, unless...''

``Unless we build a rocket!'' Philip suggested.

Raisy came from an evergreen tree, where the leaves were narrow needles, and the fairies dug their homes into them. The homes were connected by long winding staircases, but their children came and went through the windows too. The sticky resin of their tree did not freeze in the winter, and their excellent engineers had found a way to heat the apartments. Raisy too was an engineer, and while she had never heard of fairies building a rocket, she did not consider it to be impossible.

``The most important issue is fuel. If something burns fast, it also evaporates fast, so it will not be easy to find it in nature,'' contemplated Raisy.

``I know exactly where we can get fuel!'' Philip said and slid down the stem of the leaf.

\secbreak

Philip waited for Raisy at the base of the stalk, but it appeared that the elder fairy choose a more cautious way of descent. Philip watched through the looking stone as she started off carefully. But the leaves were different from the needles of the blue fairies, and Raisy did not fare well on the waxy surface. She tumbled a bit, grabbed the stem again, climbed a bit, rolled down, held on a climbed again. It did not take long before her erratic descent ended with Raisy hanging from her long blue scarf from the stem. Philip began to climb back up to help her, but he had not made it half of the way when he heard Raisy scream. His companion's scarf had slipped off the stem and was blazing a trail from the falling fairy. Philip had decide in a heartbeat. He decided to jump from the stem, grab Raisy mid-flight, and plummet together for a second time.

Her long scarf slowed down their descent, but also made it unpredictable. The rocket's rumble was a barely audible murmur by now, but the air had not settled yet and took the two fairies for a spin. They looped around the leaf stem, sped by the branch, made two loops below it, rose a little, then fell again spinning.

``Great fun, is it not, Philip?'' Raisy screamed over the sound of the air.

The world looped around them a few more times, then came to an abrupt halt. The blue scarf froze in the air, as if caught by invisible hands. The fairies had ended up on a sticky line of spider silk.

``Watch out, Philip, it's a spider!'' cried the little blue elf. ``We must get out! We have to break free! If the spider gets here we are done!''

Raisy struggled desperately, but to no avail. But her panicked efforts attracted the attention of the spider. The big black body was walking to them across an invisible thread.

``It is good to see you again, Philip,'' said the spider. ``I was very worried about you. What a wind! Fairies were falling into my web like raindrops, I could barely keep freeing them. Fortunately, I caught a nice big bug too,'' she giggled.

The terror on Raisy's face turned into incomprehension, then disbelief, and finally a wide smile.

``This is Raisy,'' Philip introduced her. ``The wind blew her here from an evergreen tree.''

Raisy found her voice and greeted the spider warmly. It turned out that fairy-eating spiders lived on her tree, and it was extremely dangerous to fall into their webs.

``Of course, friendship is much better,'' added Raisy, a little embarrassed. She was not keen to give the spider new diet ideas.

``I agree wholeheartedly,'' said Greg's mother, ``and fairies are not tasty anyway.''

After freeing both of them from the sticky silk, she showed them Greg's half-finished coat. They had a nice chat about the subtleties of knitting, and the spider even offered Raisy some brandy.

``A lot of barrels fell into my web from Solperla. They left them behind to thank me for to rescuing the fairies from the web. Here's to the great luck that we all survived this whirlwind!''

``Good stuff,'' said Raisy with a clicked of her tongue. ``This will make an excellent fuel for the rocket.''

The spider said she would never consume so many barrels, and offered a deal to the fairies. They could get all of the fuel in exchange for tying a silk thread to the rocket. The spider could then walk to the faraway tree. And if commerce began between the two fairy peoples, she could levy a tax.

The two fairies were enthusiastic. They accepted the offer, and received eleven barrels of spider brandy. As they arrived at the bottom of the web, Raisy asked for the looking stone and the travel journal and started to measure and calculate. How far is the evergreen tree? What is the best arc for the flight? How much does a fairy weigh, and how many barrels of brandy will they need?

Philip followed along at first, but then his attention drifted. Something was moving on the surface of the branch in the distance. He asked for the looking stone so he could get a better look, but Raisy would not give it up. Hanging from the web, he tried to gain a better view. He stuck his ear to the bark to see if he could hear footsteps. Something small and furry was riding toward them.

A few moments later he was running circles around Raisy with Babouche. The paramecium had tracked him down somehow, and Philip was very glad for the company. Chasing one another was much more exciting than following the complex calculations. Mary soon appeared on the horizon as well. Babouche ran from Philip to Mary, and from Mary to Philip, until the fairy boy and fairy girl reached each other.

``There you are, Philip,'' Mary rejoiced. ``Everyone in Dewington is worried for you. Good thing you were not at the top of the tree when the wind picked up everything! We would have to go looking for you to the far end of the forest...''

Philip was happy to see Mary too. He told her that he was actually right at the top when the blast from the rocket reached the tree. And he also told her what a rocket was, and introduced Raisy, who flashed a smile at Mary, but did not stop working on her calculations.

``And this is our rocket fuel,'' he pointed at the eleven barrels of brandy at the base of the spider web.

\secbreak

``Are you crazy? If a rocket that far from us created such a big wind, then yours will tear the tree from the ground,'' Mary said.

``Oh, Philip, you are scaring Mary,'' Raisy interjected. ``That distant rocket was loaded with more barrels of fuel than there are leaves in the forest. Our rocket will only have a hundred barrels.''

``One hundred barrels?'' Philip asked, surprised. ``But we only got eleven barrels from the spider.''

``I know, Philip. Unfortunately, it appears we will need to find eighty-nine more barrels.''

They went back Solperla. Many bridges hung broken, and the colorful fences were torn by the wind. One of the homes had almost separated from the bottom of the leaf, and they watched a team of fairies rescue the residents and try to pull the collapsed house back in place with ropes. One dock worker got stranded on the swinging freight transportation line, and looked up at the city anxiously. The strong building of the docks was thankfully unharmed, but hundreds of boxes and drums had rolled out from the storerooms inside, and workers were busy restoring order.

Raisy, Mary and Philip helped sort the contents of a warehouse, and heard of the damages the city had suffered. The fairies were accustomed to unexpected gusts, and most were able to hold on to something. Those who fell, were brought back by the spider. But unfortunately, the barrels of brandy all broke free, rolled out of the stores and fell into the depths. There was one unfinished barrel in the foreman's room, and he gave it to Philip in return for the help.

``If this goes on, we will not have one hundred barrels by spring,'' Mary lamented. ``And I was starting to look forward to traveling in a rocket.''

``If Solperla has lost its stock of brandy,'' Philip thought aloud, ``the surest way is if we distill it ourselves from fermented honeydew. There is a leaf under Solperla, where the aphids are put to pasture. Maybe they can give us honeydew.''

The small party descended to the leaf below the city to assess the reserves there.

``I am telling you I will sprout four more limbs, if we spend the whole day climbing up and down on the spider's web,'' said Raisy as they arrived on the leaf. Philip and Mary were ahead of her, pushing their way through between the legs of a crowd of fairies. Raisy followed them.

The fairies stood in a ring around a raging aphid. The insect was smaller than an ant, but still towered over the fairies. They all held thin ropes of spider silk, and tried to keep the unruly beast in the center of the circle. The aphid neighed and tried to cast off the ropes, but a brave fairy climbed onto its back, tied its antennae together, and tried to subdue it. A young fairy quickly ushered Mary and Philip out of the circle.

``Take care, my dears,'' she said while leading them from the circle of fairies wrestling the beast. ``Someone could trample you. What is going on here, you ask? Aphids are usually very gentle animals, but they go wild when separated from the flock. Unfortunately, the flock broke out of the pen when the wind bent the tree. This poor calf fell behind, and my sister lassoed it by the trunk. A dozen strong fairies helped her to bring it back. Not much longer until it calms down now.'' 

``What will become of us, Judy?'' an older boy asked her. ``Without the flock we will not  have anything to eat. What will we do when the winter comes?''

``All year we were preparing for the winter. The pantry is full,'' Judy reassured him. ``But we will have to tighten our belts in the spring if this calf is going to be grazing on the leaf all by itself.''

``I am Philip, the explorer,'' said Philip timidly. ``Maybe we can help you find the stray flock.''

``Where are you from, Philip?'' asked Judy.

``I am from Dewington.''

``So you live in the ant kingdom. Then you should know that the ants will capture the herd before sunset, and no matter how much we ask, they will not give it back. They will not answer, and you will not even know whether they see you.''

Philip knew the ants saw him, and Tony might even answer him. But he knew Judy was right, the ants would never return the flock of aphids. Then he remembered the old ant, who worshipped the sun and hoped that maybe he can offer them advice.

Once more they set off on the spider's web. Mary broke the silence of the climb.

``What if we cannot find more fuel? Are we going to dilute these twelve barrels? Or ask the fairies of the evergreen tree to send us some more? Or play something else?''

``But we are only eighty-eight barrels short,'' said Philip. ``I am sure the old ant will help. The fuel is almost ready for the launch.''

``Roger that, Captain Philip! And what else do we need for the rocket?'' She turned to Raisy now.

``We need a house with strong walls, in which we are going to fly. We need to attach wings to it, so we can steer, and we need a nozzle,'' Raisy listed.

``A nuzzle?'' Mary asked. ``For what?''

``When the fuel is ignited, its flame goes every which way. We need to set it on fire in a space, such that the flame can only go backward. Then it will push us forward,'' the blue fairy explained. ``The nozzle is a special tube with one narrow mouth, where the fuel trickles in, and one wide mouth, where the flame comes out.''

``But in Solperla they said the flame burns everything,'' said Philip thoughtfully. ``Will it not burn the nozzle?''

``I too heard a story from my grandmother,'' Mary said, ``in which the spider catches John and breathes fire upon him.''

``Now that is really something,'' Riasy gasped. ``A fire-breathing spider? Maybe it drank too much brandy? And what did it spin its web from so that it would not burn?''

``That is the point,'' Mary said. ``The web burned, the leaves burned, the whole tree burned, and even the earth blackened. In the end, in the midst of the soot and blackness there was only John left standing against the spider.''

``How come they did not burn?'' Philip asked. ``Are you trying to say we ought to make the nozzle from fairies or spiders?''

``They did not burn,'' Mary explained, ``so that the story could continue. But the earth did not burn either. Let us make the nozzle out of earth!''

No one could argue with this line of reasoning, so they agreed on the plan. Philip's task would be filling the brandy reserves. Raisy would build the hull of the rocket. Mary would create a nozzle from earth. For a while longer, however, they travelled together, carrying the barrels from the spider web. They marched on the branch to the trunk, each balancing four barrels above their heads. Along the way Raisy told the children stories of the family she had left on the coniferous tree.

\secbreak

``And my oldest grandson is called Robert,'' Raisy completed the list. ``He is about as big as you are, Philip! I wonder what he might be up to at this moment...''

While Raisy told them about her grandchildren they arrived at the gate of the ant's sanctuary and unloaded the heavy barrels.

``I cannot wait for you to meet them, Mary! You will get along splendidly. Come, let us see what Philip's ant friend can tell us!'' she said, and they all stepped through the ornate gate.

A wondrous golden light still filled the sanctuary, and tiny points of light swirled in the scented air. Although there were three of them now, the silence seemed even deeper than when Philip had visited alone. Raisy hugged the kids and they watched the ant for a long time without saying a word. Surrounded by the wood carvings, he touched his top limbs together in prayer. Nothing moved but the shadows of the leaves swaying in the light that shined through the gate. But the leaves were very far and their ever-changing shadows danced in vain on the ant's armor. The guardian of the sanctuary was dead. Long stalks of golden spears had pierced its forehead and shoulders. Yellow daggers emerged from his legs as well.

A yellow shard fell down and broke the fairies' daze. The shard was as big as Philip’s arm, and dropped to the floor with a puff of golden dust. Raisy was hesitant to let go of the fairy boy's hand, but a moment later Philip was picking up the strange fragment. It was very light, but seemed strong too. Its surface was covered with a thousand holes, as if someone had clumsily copied the ant's carvings. As it moved through the air, it left a thick cloud of dust in its wake. To avoid dying everything yellow, Philip wrapped it in the map of the spider web.

\secbreak

Mary slid down first through the abandoned tunnel. When her shrieks died away in the darkness, Raisy followed. Her voice faded too, then fairy laughter chimed in the dark passage. This was the signal Philip waited for, and one after another launched the barrels of brandy down the slide. Sounds of rolling and fairy laughter announced the arrival of each one, until the barrels ran out. Philip descended too, then said goodbye to Mary and Raisy. The two of them went sliding again, down into the other section of the woodworm's tunnel, and Philip let go of the barrels as well. The plan was to meet up in Dewington. With his eighty-eight barrels and Mary's nozzle they would be ready to start the construction of the rocket.

Philip unwrapped his looking stone and scanned the leaves below him carefully. He was searching for the grazing land of the ants, but another leaf caught his eye. The looking stone brought him back to the streets of Dewington. The wind had ruffled the roofs of their homes, and there was no trace of its namesake, the dewdrop in the main square. But all the buildings were standing, and after Philip traced his way back to where he started in the morning, he arrived at his home. He could not see through the roof, but he hoped his parents were at home and not worrying about him. He did not want to make them wait unnecessarily, so he resumed searching for the flock.

Fairies lived on the surrounding leaves too, and he saw an ant doing the rounds on one of them. He found two more on the branch, all of them on patrol. He follow them to another branch. Scanning this one he found a bud covered in suspicious spots. It was in shadow, so Philip could not see it well, but he suspected the lost flock could be found there.

Philip began his brisk descent thinking about how he would convince the ants to return the fairies' aphids. Judy was right, they would never listen to reason. But if he could lasso the ants, he might be able to tether them like the fairies tethered the young aphid. Or he could imitate the sound of the rocket to startle the herd, and when they flee from the bud to a leaf, he would chop it right off with the royal sword. Timed right, a gust might lift them into the air. He could loop spider silk around a branch to swing the floating leaf around the tree and into the spider's web. From here, the aphids would all tumble straight down and into the pen below.

The plan was missing some parts. For example, the royal sword was hanging on the wall of George's living room. But overall it was fairly solid. Philip was striding confidently toward the bud already. From this distance he could see that not only was the bud covered with plant lice, but also the stalk of the nearby leaf. An ant walked over Philip unexpectedly. He was ready to fight, but the ant trotted past on its huge legs without notice. Philip's knees shook as the large mass moved by, but he did not turn back.

What if ants really could not see him? Perhaps he could lead away the biggest aphid. All the rest would follow, and the ants would just stare blankly.

That is not what happened. No matter how much he pushed or pulled, the leader of the herd did not move a bit. Philip tried to lift the foot of the monstrous aphid, but it did as much good as wrestling with an ant. He climbed on its back and slapped the rear instead. The aphid did not notice this either. He sat on its head and waved in front of the eyes. He poked its nose with his feet and shouted in its ear, but the aphid only cared about the sap. How did he manage to communicate with Tony? Perhaps this behemoth would also enjoy a fairy song.

\secbreak

While Philip was struggling with the biggest aphid of the tree, Mary and Raisy had arrived in  Dewington. Both of them balanced four barrels on their heads and were rolling two more ahead of them with their feet. It is no wonder that their arrival on the leaf drew great attention.

``What is it with all the barrels?'' an alga farmer thought at the edge of the village and took a break from roof repairs to watch their arrival.

``Look, a blue lady!'' a fairy boy pointed out to his siblings as he came to a halt. It was a mistake to stop though, as his brother and sister stumbled over him from behind, and they ended up wrestling in a heap.

``Do I smell brandy?'' a shoemaker said as he opened his window. The blast from the rocket had mixed up his shoes, and a good number of them had still not found their match.

``How did they climb the stalk with so many barrels?'' a young fairy pondered in the main square. Nevertheless, he politely helped them unload, and by the time they finished, they were surrounded by alga farmers, fairy children, as well as shoemakers.

Mary told them of the plan for building a rocket, and those with nothing more important to do offered their help. Raisy organized a team to collect damaged roofs and other debris to build the rocket hull. Mary hurried to Philip's parents to reassure them.

Philip's father and mother were very grateful for the news and offered Mary fructose crystals. She could still smell the berry from which the crystal was extracted. It tasted very good after the heavy lifting. She accepted one more for the road, but in return she had to promise to return their wayward son before dark.

She ran through the main street with renewed energy and rushed past Raisy's team, who were just trying to prevent the collapse of their construction with a plant fiber. When they failed, the rumble made Mary stop for a moment.

``Go on, Mary,'' Raisy said. ``By the time you get back, we will be ready. This is only a sketch; the final structure will be much stronger.''

Mary wanted to lift their spirits, and gave them the delicious fruit sugar. She listened to their discussion of the rocket hull structure for a while, then set out on the way to the ground.

There were few stories about the ground. Grandma said it was because the fairies had moved into the trees long ago. What did they do before that? From her great-grandmother she heard they lived in a beautiful city. Its towers were as big as trees. And they had giant machinery, that did everything for them. The machines were the shape of a fairy, but their arms were thick as tree branches. The machines served them for a long time, and the fairies grew lazy and had forgotten how to work. They even forgot how to repair the machines when they broke. One day the eyes of the machines broke and they could no longer see the tiny fairies. They were no longer able to feed them, they could not build houses for them, and could not protect them from insects. The ants were waiting for this and took over the magnificent city. The fairies fled every which way. Mary's ancestors had fled into the forest. They did not know where to find food or what should and should not be eaten. The first year brought nothing but hardship, but they did not give up and learned once again to live on their own.

The trunk grew thicker and the crevices of the bark deeper. Grains of sand got in Mary's way. Some of them were as tall as a grown up fairy. Mary examined the base of each grain.  Mud splashed on by the rain glued the grains of sand to the bark, and Mary wanted mud. Crouching under a block she took out her quartz blade and scraped off a handful of clay from underneath. Shifting the tiny crystals in her hand she tried to pick out the cleanest ones. She touched them to her tongue for taste, and discarded one of them with a grimace. The other two she dropped in her pocket and resumed her trip.

\secbreak

Meanwhile, the lead aphid had made just three steps. One step forward, one to the right and one step back. Philip could not make it move by either strength or song. He tried locking eyes with it through the looking stone. Perhaps it would listen to an enlarged fairy. But it did not work out. He was digging around the bottom of his backpack now, hoping to find something that could affect his steed.

Half a dozen brightly colored quartz crystals. They did not write on the fine chitin, the tree lice did not want to eat them and Phillip juggled them in vain. The aphid did not even move an antenna.

A large jumble of spider silk. It took Phillip a lot of effort to tie this around the legs and body of the aphid, but spider silk was very flexible and did not hinder its captive in the least. It made for an excellent swing however.

Two wrinkled fruit fly wings. He unfolded these and attached them to the aphid's head with spider silk, as if they were droopy ears. Had the aphid moved its head, its fake ears would have swung around adorably.

A tassel woven from plant fibers. The fibers were dyed to different colors, and Philip's mother showed him how to weave them. He also showed it to the tree lice, and wove three of its bristles into a tassel, but to no avail.

There was the backpack itself, woven from fine plant membranes. For lack of a better idea, Philip stuck his head in it and ran around clapping and shouting on the back of the aphid until he fell down. Fortunately, he got stuck in the spider silk stretched between the legs.

Finally, wrapped in the map, there was the golden yellow shard. Philip did not know exactly what it was, but he was afraid of it. He honestly expected that the old ant would help him. But he did not get anything from it just this dusty fragment. He had heard from adults that everything had a soul. Perhaps the souls of ants were yellow. The soul of the old ant might have grown too large and broken out of its body.

He extracted the shard and shifted it from one hand to the other. Its touch dyed his palms a bright yellow.

``Philip, wrap it back up,'' an ant said behind his back. Philip recognized the voice of Tony, his former steed, who carried him from Dewington to the border of the ant empire. But it is also possible that all ants had the same voice.

``The aphid flock of the fairies ran away,'' Philip explained, ``and I have come to herd them back. I hope you do not mind.''

``I carried the sick ant up high, beyond the border of the ant empire,'' the ant said. ``Everything that the golden fungus has touched has to go. You cannot stay here. You are bad. Your hands are so yellow. Do not touch anything!''

``What if I touched something?'' Philip retorted.

``Everything will be bad! Do not touch anything!''

The ant tried to catch Philip, but it was clearly wary of the yellow shard. It went around the lice and tried from the other side, but recoiled when Philip turned to face it.

``This aphid is yours, just wrap up the fungus.''

Philip wrapped up the piece of soul fungus and climbed down from the aphid, leaving a line of yellow palm-prints behind. The ants all kept a fair distance away. Everywhere he went they backed away from him. Once he was far enough from the lead aphid, the ants quickly picked it up and took it off the bud.

Philip held his golden fingers in front, clawing at the ants to scare them off. He enjoyed not being ignored at last. On the contrary, they were all watching him now. He started running between the ants, and managed to scare one of them so much that it fell off the branch. He drew a yellow stripe on the green surface and laughed at the ants, who did not dare to cross it.

The lice were not scared though, no matter how much he tried.  They did not care even if he left yellow stamps on them. Of course, the ants were afraid of these marked lice and carried them away very carefully. Philip felt bad about scaring the ants, but could not stop playing this game. He was running around and stamping the aphids until the whole herd had been marked with yellow spots and the ants had obediently carried them all off.

``I am sorry,'' he said to Tony. But the ants had backed away from the bud, and Philip was left alone.

\secbreak

Mary reached the base of the tree. The trunk was at its widest here and the roots burrowed into the ground. She managed to find some fine clay on the way down, but she needed at least thrice as much. Before descending to the surface she looked around from atop a thick root. It was a scary thought to leave the tree. Detritus covered everything around her. Dry, dead leaves. Fungi gnawing on their surfaces. The leaves at the bottom were in the worst shape. They might have fallen off last year. If someone had dared to approach them, they might have found ruins of fairy cities from the old year.

Mary heard a noise. A sand lizard ran through the detritus, pushing whole leaves to the side along the way. A large animal like that could break Dewington right off the branch. The lizard ran towards the setting sun. She saw the dark silhouette of an even larger animal in front of the sun. A deer was tearing off a twig from the next tree. As she watched it chew patiently, Mary could only hope that no fairies lived on those leaves.

She gathered her courage and descended further on the root. The bark was breaking up, and she walked in its long grooves. The grooves were deep as canyons. Remains of the old bark watched over them. The highest parts of the bark were from the first years of the tree. Worn and dried by countless winters and summers. They had long lost their defenses against fungi, and a lacework of colorful lichens cast shadows on Mary.

``Little miss fairy! Fairy girl! Where to, where to?'' a voice called down from the lichen. Had it not called, Mary would not have noticed the fat gray mite. His obese body rested on a couch woven from the mycelium. His eight feet hung around the edges of the recess. One of them lazily dug into the dense weave of fungal filaments and pulled out a lump of green alga from the bottom layer.

``I will answer you if you can answer a riddle for me,'' said Mary. The mites were famous for never worrying about anything. They were not much bigger than a fairy but were as strong as an ant. So they had no one to fear and could take anything they liked. They lived their comfortable lives peacefully and were always up for a game. ``What are clouds made of?''

``Oh, little fairy, to ask that of a mite,'' the mite above laughed and swallowed the lump of alga. ``My cousin was a famous traveler. The wind took him everywhere, even above the clouds,'' he continued with his mouth full. ``The cloud is nothing more than a lot of water droplets that the wind holds in the air. They may be about the size of your head, little girl. If they grow big enough to fit you, the wind can hold them no longer and they fall down. That is the rain!”

``I will be a traveler too when I grow up,'' said Mary, ``and I will go up above the clouds. I will see then whether you were right or not. I will come back if you were wrong!''

``I will wait here, sweetie. But now tell me, where are you going? The fairies live on the leaves above. Have you perhaps dropped something?''

``I am searching for clay. We will build a rocket nozzle from it.''

``You want to search among the roots?'' the mite asked in surprise. ``Did you remember to bring your lantern? It is pitch dark down there, little fairy. You know what? If you can answer my riddle, I will give you a lantern. I found it between the gills of a milk-cap. A firefly must have lost it. It can be yours if you answer right. What does it mean when a firefly is blinking in yellow?''

``It is signalling a turn,'' Mary said right away. She got the lantern from the mite too. It was a hairball that smelled like a mushroom and glowed faintly in the twilight.

Mary thanked the mite for the useful gift and continued on her way. The root curved to the right, curved to the left, then curved down. Mary carefully followed it down under the big black lumps of earth. She saw nothing at first but then her eyes became accustomed to the darkness. The air was musty with the smell of mold and bacteria working in the soil. Much moisture was trapped in the rich structure of the ground and Mary was wary of falling into a muddy pool. It would be the end of her pretty dress and of the clay collected so far.

As the root passed under the ground, fine hairs stemmed from it. They ran out into the mysterious world of the soil and absorbed all the moisture and nutrients that the tree needed. Mary descended further. The topsoil had a lot of decaying plant matter and tiny creatures were having a feast all over it. It would have been difficult and gross to push them aside to reach the mineral clots.

Deeper still a long discarded pod of chitin was blocking Mary's way. An insect larva wore it once, who grew large chewing on the root and had cast off its skin. The root has grown thicker since then and pressed into the abandoned husk. Mary put her lantern, the glowing knot of hair, on her head as a hat and pulled out her sharp quartz knife. She pierced the barrier and cut a round hole into it with a quick motion. As she was rolling up the patch of skin, she saw a red light deep below. She fumbled in surprise and got tangled in the thin chitin. She struggled to break free, and by the time she cast off the larva skin, she was tumbling down into the hole she had cut.

To stop her fall, Mary stabbed the knife into the root surface rushing by. She slowed, then stopped and finally stood on a root hair. A clear drop of water seeped out from the scratch and fell on her head. She shivered. Where did the red light come from? It was nowhere to be seen now.

Mary balanced herself on the narrow root hair. The white path wound among large, cool nuggets. A patchwork of black hyphae covered their sides and filaments stretched in the space between them too. The sharp knife opened Mary a path into the darkness.

She had just gotten used to shredding the black strands like a windmill when they ran out. Her arm swung at the empty air for a moment, then she stopped and looked around. The strands stayed on the right because they found nothing to digest on the left. The nugget to the left shimmered bare and gray. Clay! The quartz knife went to work again and Mary's pockets started filling out.

\secbreak

Meanwhile, Philip arrived to the ranch under Solperla. There was a great deal of excitement there. They had found a big aphid, to the head of which someone had tied a pair of wings. And as they drove it toward the farm they saw another one. When they threw a lasso on that aphid, an ant had just carried up one more. He put it down at the border of their empire and refused to let it climb back. He stood in its way, until the fairies led it off to their ranch. This went on all night, and the flock the ants returned was twice as large as the flock they had lost. And on the side of each aphid the yellow prints of five tiny fingers gleamed.

Once they saw Philip's yellow hands and heard his story, all the fairies, big and small, celebrated him. They set a long table right away, and everyone brought something delicious from their pantries. With such a large flock they no longer feared the winter. They served soured insect egg soup and fried alga rolls for starters. The next dish was balls of cheese wrapped in thin slices of smoked aphid ham. And while the fairies feasted, the dessert was prepared as well. They cut a large pollen in half and filled it with fruit pulp. One half was prepared for the children with fresh pulp; the other half for the adults with partly fermented pulp.

The feast lasted all night, but Philip still had important things to do. He asked Judy for help, and together they milked all the lice. They gave enough honeydew to fill up all barrels.

``What a big flock you have brought us, Philip,'' Judy mused. ``We need to build more barrels. We will need a larger pen too. It will be a lot of work. We cannot let our young ones go to Solperla to try their luck now. The leaf may turn out to be too small too. We will have to find two leaves in the spring. If they lay many eggs, perhaps even three.''

When they ran out of barrels, they collected the honeydew into baskets, tablecloths and sheets. Overall they got more of it than there was water in the dewdrop of Dewington. The only remaining question was how they would ferment and distill all of it.

``It is good sweet honey the new lice gave,'' said a bearded old fairy, ``and the evenings are still warm. If we add the yeast now, it will be fizzy by the morning.''

``But how will we distill it?'' asked another fairy, who could have been his twin brother. ``You cannot kibble that much dew mead by hand.''

They argued on, and Philip learned of more tricks of the distillation process, than he ever could have imagined. For instance, after fermentation the dew mead was usually kibbled into small beads so that it would evaporate quickly. They were trying to figure out something more efficient, but everyone agreed on one thing. If they wanted to let the honeydew ferment by the morning they had to add the yeast now. All the fairies, who were on a short break from the celebrations, helped with this. And Philip headed home.

\secbreak

The clay weighed so heavily on Mary's pockets that it was pulling her skirt down. Ingeniously, she fashioned suspenders from a few black fungal filaments to hold it up. The nugget of clay she had been mining was covered in scratches. Her hard work had stripped off the surface three fingers deep. The clay was very fine. Neither grains of sand nor plant matter-digesting hyphae were to be found in it. This was exactly what Mary needed for the nozzle, and she was very glad to have found the nugget.

One pocket was full and the other was getting there too when, to Mary's surprise, red light traced the knife's path. The dim radiance had to have come from somewhere. To find its source, she twisted the knife to enlarge the hole. No matter how much she peeked she only saw clay illuminated in red. She continued to work until the hole grew as big as her hand.

Sticking her face to the opening she could now see that the nugget was hollow. She had cut a funnel-shaped hole into a span of wall. On Mary's side the hole was as big as her hand but on the other end it was as if she had poked a hole with a finger. As if she had poked a hole with a finger through the living room wallpaper of a fairy. She saw the back of a couch. The seats looked toward a fireplace. Compressed blocks of cellulose smoldered inside and radiated a warm glow upon the room. Neatly framed pictures lined the mantelpiece, mounted on the wall above them the scary head of a worm stretched its mustache toward Mary. The red-striped wallpapered walls curved outward a bit, but the room still had corners. In one corner a well-shaped fungus grew in a clay pot. The yellow mushroom was practically glowing in front of the red wallpaper.

A fairy stood up from the couch and turned to face Mary. His outline was gleaming from the light of the embers. He was tall and strong. The wide shoulders carried a bald head, but on both sides a thick mustache broke its circle. His mustache was just like that of the trophy above the fireplace. A black cloth covered his right eye. The left one watched the hole closely. As Mary recoiled, the stern face flashed green from the light of her glowing hat. The fairy girl screamed and ran.

She did not run far before the hyphae she had cut earlier slapped into her face. She lost her balance and almost fell off the narrow root hair. She clung to the web of filaments and hurried on, grabbing them every few steps for balance. Her heart beat so loudly she could not hear anything else. But she imagined that the fairy with the big mustache had knocked down the wall and was furiously galloping behind her. She dared not look back, not into the single eye flashing in green. She just stumbled toward the root, away from there, back to the leaves, back to the well known world of Dewington.

She thought she was lost forever in the black web of hyphae, when she finally saw the pale walls of the root. But just as she started to run, a terrible shadow formed in front of the root. The one-eyed fairy was riding a long slithering mass as thick as her waist. In his eye the cold reflection of her green lantern danced. The blood froze in Mary's veins; she was paralyzed by fear. The monster pulled a red light from under his jacket and held it up high.

He looked just as evil in the red light as Mary had imagined. Or at least almost as evil. A little less evil, because the mouth under the thick mustache formed a wide smile.

``Steady, Anaconda!'' he soothed his steed. ``You are scaring our guest.''

\secbreak

The sun was starting to set. In the long shadows that were filling the grooves on the bark Philip saw serpentine shapes.

A short while earlier he knew no fear and swung from one thread of the spider web to the other, whistling a song. But in the sanctuary, among the intricate carvings, he fell silent. As he had hoped, he received help from the peculiar ant. But he did not quite understand what happened. The ants said he did something bad, but the fairies said he did good. He did not know what his parents would have to say about it. As he turned the thoughts in his mind, he felt relieved at times and guilt ridden at others. But, as the shadows grew longer, the pride waned and the guilt waxed. Do the ants have a full pantry? Will they have something to eat in the spring?

The world of the bark is busy at dusk. The stalking forms of the night have risen but the alert beings of the day have not retired yet either. Everyone was hunting or being hunted at this hour. Protozoa were running from waterbears. Mites were wrestling nematodes. Hyphae snatched the fallen. And the ever-changing shadows of conscience chased Philip.

He ran from the long shadows and wet sounds as fast as his legs would carry him. He wanted to be back in Dewington as soon as possible. He was tired now, but if he slowed down the sounds came closer. Sticky hyphae caught his foot in a ditch. While he pulled it free, the shadows caught up. And they passed him by. An army of diversely shaped protozoa and other small creatures slipped and crawled by him. They ignored the fairy as if they were hurrying to Dewington as well, so they would be home by dinner too. Philip freed his legs and looked after the hairy, sticky, tentacled crowd in bewilderment.

Unexpectedly, a shadow engulfed him from behind. So that is why the protozoa fled! A big yellow wall rose above the cliffs of the bark and approached Philip fast. It slowed down, stopped, and then took off again. Philip stopped staring at it and broke into a sprint. The slime mold must have crawled into a dark, dank corner during the day, and once shadows covered the bark its time had come. The huge, throbbing cell pushed itself forward with each pulse and digested everything in its path. That is why the tiny inhabitants of the bark were running. A dozen fairies could not have stopped it.

Philip tried to keep to the last sunny spots and hop across shadows. But when approaching a big outcropping of bark he had to step into the dark. It was dangerous to run blindly on the uneven ground, but he could not slow down. The slime mold picked up speed in the cool shade and was on Philip's heels with each pulse. Philip ran close to the cliff, which offered some shelter from the slime mold. But the cliff ended, and Philip ran through the open field. He had almost reached the end of the shadow when he stepped into a ditch and stumbled. He could not jump back on his feet either because his shoe had become stuck in the ditch. This was the slime mold's chance, and its yellow wall rushed toward Philip.

Suddenly, a big ball of fur popped out of nowhere and jumped against the wall. It bounced back like rubber, but the impact also stopped the wall for a moment. The ring of waves spread on the surface of the slime mold. The waves did not get far before the ball of fur slammed into the wall again.

``Run, Babouche!'' shouted Philip when he managed to untangle his foot. Paramecium and fairy ran side by side from the yellow wall. Fortunately, the bark became smoother and the shadows fewer as they approached Dewington. The light of the setting sun forced the slime mold to stop there, and the two friends merrily chased each other until they got home.

\secbreak

The dewdrop had long ago evaporated from the main square. The morning’s crowd of fairies had evaporated also. There were no vendors, and no one came to fill their canteen. At dusk the streets emptied; the doors and windows shut. Philip saw only an old fairy sitting on his porch, but he did not return his greeting. He must have fallen asleep and would only wake up when the early chills of the autumn pinched him.

Yet the square was not empty. A big pile of cellulose and chitin littered it. Plant fiber and spider silk wove through the heap. Twelve barrels of brandy lay strewn about. And from one of the barrels a monstrous snoring was heard. The barrel rocked back and forth lazily to the rhythm of the snore.

``Hello,'' said Philip timidly.

There was a pause in snoring, then the barrel resumed rocking. With Babouche by his side he moved closer and peeked into the barrel.

``Raisy!'' he shouted.

``Leave me alone,'' snorted the barrel. Babouche was excited to hear the familiar voice and jumped in by Raisy. It must not have been comfortable for either of them because a lot of tossing and turning followed. In the end the barrel began to roll and hit the pile of building materials. Raisy tumbled out of it with Babouche on her head and lay spread out on the surface of the leaf.

``Captain Philip,'' she perked up a moment later, ``we have evaluated two dozen different rocket hull designs, sir. And,'' she added almost inaudibly, ``emptied a dozen barrels of brandy in the process.''

``This is great news, navigator Raisy,'' responded Philip. ``Have you found the perfect design then?''

``We have... some more ideas. And tell me Philip, how did it go with the ants? Did you get them to return the flock?''

``Yes. And they returned more than had been lost,'' he boasted.

``That is great news, Captain!'' she said. Then her eyes widened. ``What? Did they really return the lice? What did you do, Philip?''

Philip told her what had happened on the pasture of the ants. To share the story they climbed on top of the collapsed buildings and enjoyed the fresh air. Babouche curled up on their feet and, faithful to his name, kept the tiny toes of the fairies warm. Raisy listened carefully to how much the ants had feared the golden powder and how they carried the flock up to the fairies. When Philip went on to describe the feast, she got rather hungry. But only a small clump of dried alga remained in her satchel.

``A slime mold so high in the tree?'' she gasped when he reached the end of the story. ``You were lucky that Babouche had found you. I also met a slime mold when I was about your age, Philip. My brother Gil was even younger, but a true little demon. Together we ambushed a flea and rode around the tree on its back. But it is easy to slide off of its smooth back, and Gil clowned about until it threw us off with a jump. We landed in a shady cleft in the bark, and laughed so much we could not see from our tears. Suddenly Gil stopped laughing. When I noticed that I was laughing alone I opened my eyes. The remains of a mite lay beside us. Something had completely stripped the exoskeleton. Under our feet the decaying cell membranes of protozoa covered the bark. We did not know how these tiny creatures might have perished, but we were very scared. We tried to tiptoe out of the crevice, when suddenly...''

The stars had disappeared from the sky during her story, and the darkness deepened. When she came to the scariest part lightning flashed. The lightning illuminated a terrible serpentine form in the main square of Dewington.

``Ah!'' screamed Raisy and Philip. They staggered from the sight of the monster and tumbled from the top of the experimental rocket hull. The thunder and shouting woke up the old fairy sleeping on his porch too, and he stared into the darkness. By the next lightning he too could see the half-snake, half-fairy form. He stumbled over his bench, fled into the house, and slammed the door. And then shut the window too.

``This is scarier than the slime mold,'' said Raisy from one of the barrels. Philip snuck back to the top of the pile and stuck his head out to peek at the terrible squirming form. The clouds had covered the moon and the stars, and everything was black. But Philip had a good eye, and different things were different shades of black.

The winding form had to have been that of a large nematode. Three dark figures were riding on its back. One was a big, brawny fairy; another was a small, fragile fairy. But the largest figure sat between the two. Shapeless arms, tentacles and claws protruded from it in every direction. It really was scarier than the slime mold, but Philip boldly crept closer. He heard a whisper from the black riders.

``Did you see Raisy tumble down?'' asked one.

``I did! And did you see Philip's face in the lightning's flash?'' asked the other with a suppressed chuckle in her voice.

Philip recognized Mary's voice right away, but he did not want to miss a good chance for a scare. In the dark anyone could surprise anyone. Mary and her two mysterious companions on the back of the worm slid toward the center of the square while Philip took a small detour to get behind their backs. He put his empty backpack on his head and grabbed the unsuspecting Mary.

A great deal of screaming, wrestling, and chasing was the result. By the time they were both so exhausted that they could no longer be scared, Raisy had also emerged from her barrel, and Mary introduced her companions.

``This is Anaconda,'' she pointed at the ever-winding worm. ``And this is John.''

The strong fairy climbed off his steed and pulled out a glowing red lantern. His left eye glowed in the light but the right eye was covered with black felt. Below a big nose his long mustache covered a friendly smile.

``I am not the famous hero,'' he said, ``just his namesake. I apologize for scaring you. It was Mary's idea.''

``I had to scare someone after being scared myself,'' Mary said. ``John lives underground and is a fearsome hunter. When we met I was so afraid of him, I wanted to run away. He just wanted to talk, however. So many exciting things had happened to him under the ground, but he is the only fairy there, and there is no one to listen to his stories.''

``And your other companion?'' Raisy said.

Mary pulled out her green fur lantern and shone its light on the last rider. The misshapen figure was neither a fairy nor any other creature. A big pile of clay was molded into all sorts of appendages. They had used strips of phloem fiber to tie it to Anaconda's back. In the green light all its terrifying features had disappeared. Someone had even sculpted a big smile on its face.

``This is Jimbo,'' beamed Mary. ``Until recently, he was the wall of John's living room. But today he has decided to become a nozzle!''

Neither Philip nor Mazsi understood much of that of course. Mary had to tell them everything on their way home. Mary's parents invited John inside and Philip's parents sat Raisy down to their dinner table. Conversation filled the two small houses on the tip of the leaf. The children told of their adventures, and the polite travelers compared the dark world of the soil and the distant world of the pine tree with the green leaf of Dewington. Slowly the light of the lanterns faded and everyone grew curious of the next day. They said goodbye to each other and all went to bed.

\secbreak

Philip turned in his bed twice, then had a better idea. He picked up the looking stone from his nightstand and snuck out to the back of the house. Mary was sitting on the edge of the leaf already, her legs dangling above the abyss. He lent her the looking stone and gazed thoughtfully at the black leaves sprawling below.

``Mary, where would you like to fly the most?''

``To Raisy's pine! She promised to teach me how to bake a resin cake.''

``What about after that? If the rocket works, we can fly it anywhere.''

``Oh, that's right,'' agreed Mary. She started to think on it now. ``There is the raspberry bush by the big rock. The wind always blows delicious smells from there, right? Do you think it could take us there?''

``Of course it could! We would have to be careful with the landing. We would not want to get caught on the sharp thorns. But the leaves are safe. And where would you fly from there?''

``Back to Dewington. We could bring back a whole berry, and everyone could have some of it.''

``All right. But after that we will fly up to the tip of the old tree that stands on the hill top. From there we would see trees that we cannot see from here. And we would go on until we reach the edge of the forest.''

``And maybe we would find another forest there. One which is full of raspberry bushes. And blackberry bushes.''

That is how the two little fairies planned their trip until they grew sleepy.

\secbreak

Philip dreamed that he was little. As small as one of his eyelashes. He was in his room, adventuring within the forest of the soft fibers in his carpet. Suddenly it became dark, and as he looked up he saw that Mary was sitting on the bed. They were in Mary's room and not Philip's.

Philip climbed to the top of the carpet and leapt from one fiber to the next. From red to yellow, from yellow to white, from white to blue. Then he realized that if he jumped on the colored threads in the right order, his shoes would become brighter. Mary held the looking stone in reverse, so she could examine the miniscule, radiant shoes. The only light was now coming from the shoes, and the tiny Philip cast a giant's shadow on the wall of the room. The shadow was so big that it could lift Mary in its hand.

Philip, the shadow giant, rode on the back of a giant ant. He wore a golden yellow robe and his steed was a golden yellow too. But Mary saddled a lizard and met the army of golden ants in battle on the plain below the leaf. The lizard swept away dozens of ants with its tail, but then made peace with them. She helped up the little ants and fed them raspberries from her  saddlebags. The ants in turn helped her build a huge machine shaped like a fairy. Its foot was bigger than a whole leaf. Its shoes were built from a dozen large snail shells. Its leg was a tree trunk and it was so high that it could reach the lower branches of the tree while standing on the ground. On top of its neck it wore the smiling head of Philip.

``But what is this giant machine good for?'' Mary asked.

``For playing tag!'' Philip exclaimed and threw himself upon the lizard. But the lizard was nimble and the giant's hands grasped only dry leaves. He held the leaves to his eyes to see who dwelled on them, but did not see anything. The lizard ate the leaves. It ran circles around Philip and cleaned up the forest floor in his path. As it sucked up all the leaves it grew bigger and bigger. When it got big enough, Philip sat on its back as well and they rode among the trees.

Soon the lizard became as big as a tree, and Philip jumped from its back onto the top of their tree. Philip balanced on the uppermost leaf of the tree just as a rocket rose from the valley. Its light shone throughout the forest, and all the leaves fell off. Philip also began to fall, but the rocket quickly changed direction and caught him mid fall. The rocket was big as the giant lizard, covered in complex winches, ropes and arms. Mary opened a trap door and let Philip inside. They flew up into the sky and flew to the sun and the moon. It was autumn on the sun and all the leaves were yellow. It was winter on the moon and white snow covered the trees. Only one tree was green, Raisy's pine. And the nice fairy lady waved at them from her round window that was cut into the side of one of the needles. They skillfully landed on her doorstep, but since everything is upside down on the moon, when they got out Philip began to fall toward the Earth. Mary did not understand why he was falling toward the Earth and drank a cup of tea with Raisy.

Philip was falling and falling and getting smaller. When he fell from the moon his foot was as big as Dewington. But when he reached the branches of their tree, he was only as big as an ant. When he fell on the roof, he shrunk to the size of a fairy. He fell right into his bed and sat up. His mother offered him a cup of tea for breakfast.

\secbreak

Raisy was sitting on the terrace of a café in the main square. A sheet of cellulose paper covered her small, round table like a tablecloth. The calculations were already flowing off the edges of the table, but the pencil was still busy in her hand. One formula led to another, and her model of the behavior of different rocket hulls became more accurate. She calculated the forces which would affect various parts of the hull during take-off when they built beams one way or another. A hull of greater weight may be more powerful, but would also have difficulty supporting its own weight. When she was young, she was taught in school how the different varieties of cellulose and chitin held under pressure. During her work as an engineer she learned about many ways to strengthen a structure. Now she was making calculations to know how each would work in this case. After all the unsuccessful experiments last night, she preferred to do the analysis on paper.

``Let me see where this derivative becomes zero,'' she muttered when Philip joined her at the table. ``I am almost done with the calculations, Philip. No need to worry about the rocket hull. I will be ready by noon at the latest. I will drink one more coffee.''

Philip did not want to disturb her. It rained overnight, and the raindrops washed away the half-built rocket and the empty barrels. Nothing but a huge ball of water sat in the middle of the main square. It scattered the light from the rising sun in every direction, but it was especially generous to a bench on the edge of the square. It cast a shadow on the houses around the bench, but the light that it took from the houses it gave to the bench. When the sun rose only the old fairies who woke early basked in its warmth. But over time a group of children had joined them. In the end their old ears started aching from the squeals of the younglings, and they let them have the bench to themselves.

As the sun rose higher the hot spot slowly moved closer to the center of the square. It had climbed off of the bench, and the crowd of children were trying to push the bench back under it. A blonde fairy boy took his chance for a bit of sunbathing while the others struggled, causing a tug of war to erupt.

Once they had made peace, Philip helped out with moving the bench. Soon they could all enjoy the comfort of condensed sunlight. They had worked up a sweat in the effort, but the tiny droplets quickly evaporated from their brows in the heat.

``That's it!'' Philip exclaimed. ``We can easily distill the mead here!''

``The what?'' asked the blonde boy. But Philip was already on his way to the shepherd fairies.

\secbreak

At the outskirts of Dewington Philip stumbled into Mary and John. Mary was sitting on Anaconda's back, and John, with the reins in his hand, was teaching her how to ride. Philip saw the nematode in daylight for the first time. Its skin was bright red and smooth like a drop of water. A girth of sticky hyphae held the saddle on its muscular body, and John explained how to control Anaconda by the bridle on its nose.

After Mary was done, Philip too learned how to ride the gentle worm. Meanwhile, he told Mary and John of his plan to distill the rocket fuel in the focal point of the big drop in the main square. Mary in turn explained how the nozzle would be prepared.

``We will need two tamed nematodes. One of them slides around in a small circle while the other one makes a larger circle around it in the opposite direction. Their smooth skins will shape the wet clay we feed in between them into a thin ring. As we add more clay, the pressure from the worms will squeeze the moisture out of it, and a solidifying wall of clay will rise between them. We carefully lead both worms to gradually widen or narrow the two rings. This way we can build the nozzle in the exact shape that Raisy has engineered.''

John and Philip shared appreciative glances. Mary had indeed put a lot of careful thought into the method of nozzle construction. They could use the same method later for building large tanks and kegs too if they wanted to. With more worms and enough clay they could even use it for constructing buildings.

They all took off on Anaconda's back to capture the nematodes who would shape the nozzle. Even with the three fairies on its back, the bright red worm slid on the uneven surface of the branch like the wind. The fairy kids enjoyed the rush, but all too soon they reached their destination.

Moss grew on the northern side of the tree even at this height. In the tangled forest of moss stems moisture was trapped, and the dark water was teeming with life. Tardigrades frolicked, amoebas exercised, and a mosquito larva filled one of the larger droplets entirely by itself. And on the wet clods wild nematodes slipped from shadow to shadow.

``They move in swarms, you see,'' John pointed at the worms. The dark, dank world under the moss was his world. Each animal reminded him of a past adventure. Philip and Mary listened in awe. ``This yellow-striped swarm is too wild. Can you see the teeth? It would rather tear my arm off than let me ride it. The white ones in the drop over there are easy to handle and very good swimmers, but they cannot deal with dry land. But up there, high up in the moss... Do you see the red flashes?”

Green light filled the forest of dark stalks. The moss leaves bathed in the sun above and covered the blue sky entirely. As Mary and Philip strained their eyes, they saw something red appear and then disappear immediately.

``Those are relatives of Anaconda. Agile, strong worms. They love alga. Come on, let us collect some alga. If we trap the worm and then hand feed it, it will turn into a tame steed right away.”

They fished out green, fist-sized balls from a bright drop of water. Philip tasted one, and it was good and juicy; just a little bitter. John also taught them which hyphae make a good harness. This fungus was a danger to the wild worms, because they could easily get stuck in the adhesive threads. They carefully coiled a long hypha and started climbing toward the moss leaves.

The red worms avoided them at first, but could not resist when they saw the beautiful green balls of alga. They circled the fairies and snatched the algae from their hands with lightning fast movements. John tied the hypha into a loop and held it in front of the alga in his other hand. When the worm struck the alga he pulled on the rope, but the worm had avoided the noose or was just too fast. John loosened the noose and tried again. The second time he got lucky, and the sticky thread fastened on the midriff of the worm. John paid out some rope until the worm ended up orbiting them on a leash.

``And now we carefully draw it in,'' John said. ``It could easily drag off all three of us, but the moss stems are even stronger. I tie the thread around a stem like this,'' he demonstrated. ``And note this knot. We can draw on it, but when the worm pulls from the other direction it will hold.''

He used the wily knot to pull the worm gradually closer. The other members of the swarm recognized the trap and bolted. Left on its own, the scared worm tried to escape but got tired and gave up. Trembling, it awaited its fate. Philip held an alga to its snout. The worm sniffed it uncertainly then accepted it. Philip fed it some more and scratched its back like John advised him. The nematode calmed down and let them turn the loop around its back into a plain saddle and tie a bridle on its head.

Philip named his new friend Rocket. Anaconda gave it a friendly sniff and after a bit of hesitation Rocket allowed Philip to lead it on a leash. It was slightly slimmer than Anaconda, but it still had the strength of several fairies. Soon it allowed Philip to sit on its back, and until Rocket got used to the reins they zigzagged between the moss stems with abandon.

Once they learned to understand each other, they set out to catch a worm for Mary. On his nimble steed Philip helped steer a swarm of red worms toward John and Mary.

``Good luck,'' he waved to Mary. ``We will meet in Dewington. I will bring down the mead and by the time the nozzle is completed we will have the fuel as well.''

``Good luck, Philip,'' they waved to Philip from the ring of red worms as he rode away on Rocket.

\secbreak

Philip's knees were a little weak when he dismounted Rocket on the shepherds' leaf. The speed of the worm was terrifying in the rifts of the bark, but they arrived safely. The fairies of the leaf admired his shiny red steed and greeted Philip cheerfully.

``Captain Philip,'' said Alexander, one of the mustachioed masters of honeydew fermentation. He picked up the habit of addressing Philip as ``captain'' from Raisy, but a playful esteem rang in his voice. ``I took a look at the barrels just now. They got good and smelly. The honeydew fermented finely. The only problem is that we could not knead this much mead in the whole day.''

``And we will not have to,'' Philip said while tethering Rocket to the stables. ``I think we can distill it in Dewington. There is a big drop of dew on the main square of our leaf which collects the sun light. If we put a barrel in its focal point it will warm up right away, and the spirit will rise up.''

``What do you make of that, Alexander?'' asked Alexander his partner, with whom he shared not only the task of making brandy but the name as well. ``Could we distill spirit like that?''

``It could work if we keep stirring the juice. If we hit the right temperature, the spirit will part from the water.''

A little later they had exhausted this topic, and the discussion turned to the question of how one hundred barrels full of mead could be transported. Half a dozen lice could have carried them, but running a caravan through the empire of the ants was a great risk. Philip did not know how many barrels Rocket would be able to carry, but certainly much less than an aphid.

``Nice nematode,'' Greg spoke from behind Philip's back. Philip turned in surprise to see his spider friend hanging upside down on a fine thread of silk. Gref focused his eight eyes on Rocket.

``Good morning, Greg,'' Philip greeted him. ``I hope last night's rain did not soak you.''

``We took shelter under the branch. The web always fills up with food before the rain, so we do not regret the inconvenience at all. Mom is cooking a delicious lunch right now. Want to play a game until then?''

``Did you see how the fairies in Solperla swing their cargo from one end of the leaf to the other on threads of silk? Let's play that! We will be the fairies, and these barrels will be the cargo. We have to deliver them to Dewington below.''

``To Dewington?'' Greg asked slowly swaying.

They hatched a plan together. Dewington was not exactly below the pasture, but was visible from its edge. They piled up the mead-filled barrels, bowls, table linens, and blankets at one end of the leaf and Greg wrapped them into a neat package. They attached the package to the other end of the leaf with a long thread of Greg’s silk and let the loose thread fall off around the edge of the leaf, so that it would run below it.

``Are you ready Greg?'' asked Philip. They had pushed the cargo to the edge of the leaf together and only needed one more nudge to let it go.

``Come on, let's go,'' Greg replied. With another shove the center of mass of the package was over the edge. The bundle of barrels and sacks slowly tumbled. As it rolled over, Philip and Greg climbed on it, and when the spider's thread went taut, they were sitting on the top.

``We are swinging in the right direction, Greg!'' Philip shouted as they flew. ``But our swing does not reach all the way to Dewington.''

``We are just getting started,'' Gred replied. ``Check out how a spider swings!''

Greg added more and more silk to their thread. He always added the extra length as they were reaching the highest point of the swing. He skillfully took advantage of air movements too, and tightened and loosened the line in a way that kept accelerating their cargo.

``Here we go!'' Philip cheered. ``Look, Dewington right below us!''

``Prepare for mooring!'' said Greg. The next time they swung above the target, he threw himself fearlessly off the shipment. Philip reached for him in a moment of panic, but then understood what the little spider was doing. Greg started a new thread off the swinging cargo and anchored the other end to the leaf when he landed in Dewington.

``Hold on!'' he shouted from below, but it was too late. The new thread went taut, restrained the swing of the package over the village square, and Philip tumbled off of it. The fairy would have plunged straight into the sparkling dewdrop if not for the webbing that covered their cargo. He managed to hold on to the knot of spider silk, and was dangling at the bottom of the package.

The package of hundreds of barrels of mead was bigger than the dewdrop. All eyes on the main square were on Philip.

``Philip, do not squirm,'' Greg said, and began to climb up. ``If the anchorage breaks, you will be swinging there all day. And I get a swimming lesson in your dewdrop!''

Philip obediently stopped moving and hung forlornly from the package. Greg arrived, and attached a new thread to a barrel. Not sparing a glance for Philip, he descended on the thread while carefully avoiding the dewdrop with the use of air currents. He tied the tether to the top of a house and climbed back on it. He extended three more threads the same way and moored the shipment perfectly. When Philip felt that not even a butterfly would be strong enough to break the package free, he climbed over to a tether and descended to the leaf. The spiders loved hanging from a silk thread all day long, but it was not for Philip.

``I cannot believe my eyes,'' Raisy welcomed them. ``That's enough brandy to fill a dozen rockets, Philip. And such graceful delivery...''

``This is not brandy, but mead,'' Philip corrected her. ``We still have to distill the spirit and collect it somewhere. Over there… is that Mary?''

Mary looked as if Jimbo, the clay monster, had come to life. The first nozzle that they built was too soft, and when it started to collapse Mary tried to hold it together. Unfortunately, they had to start over, but nothing more than a little bit of time and the clay that had stuck to Mary was lost.

``Yes, it is me. Over there is Raspy,'' she pointed at the clay-covered worm circling the unfinished nozzle, ``and on the inside is his partner, Cranny. We are molding the shape very carefully to avoid defects. But we will be ready soon.''

``May I peek inside the nozzle?'' asked Greg as he landed.

``No,'' replied Mary. ``You did not help Philip to climb down.''

``But he was hanging so comfortably. I hang like that all day.''

``But he is not a spider!''

Greg and Mary continued the debate while Raspy and Cranny shaped the clay.

\secbreak

``I have finished the calculations, Philip,'' Raisy said. They found a place to sit down among the heaps of notes covering the terrace of the cafe. Raisy swept all but one page off the table. She smoothed this one neatly and turned it to Philip. ``The results for the various constructions. Unfortunately, we get a number that is less than zero for almost every structure. These would break up in the air. But this one works.''

Columns of numbers were accompanied by tiny illustrations depicting the structures.

``A sphere!'' said Philip as he found the winning variation. ``We need to build a sphere then?''

``And not just any sphere. Only cold-forged chitin is strong enough. If we just glued or riveted plates together, the chitin would fall apart,'' she said pointing to the next row of the table.

``I know such a sphere.''

``You do? Who has built it?''

``Balthazar, the caterpillar,'' said Philip.

They both rose up and went to have an audience with the king. The evening rain had soaked the dead surface of the Stain, so it was soggy now, but  at least there was no risk of sudden cracks. A few black bacteria were grazing around Balthazar's severed head. They scattered when Philip and Raisy reached the door and knocked.

``Well, Philip,'' George said when he opened the door. ``I was not expecting guests today. The stain is so muddy. But come on in. I am George, former king of Dewington.''

``I am Raisy, a friend of Philip's. The gust from the rocket launch yesterday has flown me here from a distant pine tree. The children are helping me return home. We are building a rocket of our own and flying to my home.''

George's mouth dropped open.

``I have traveled a lot when I was young. I have even been to a branch of the neighboring tree. But the pines are on the other side of the valley! Unless the wind that carried you here is kind enough to take you back, I am afraid there is no way to the pines.''

Raisy just smiled and pulled out a roll of paper. George sat them at his table, made a pot of sweet tea and listened to the grand plan. Although he was not taught at school, he had a sharp wit and asked many serious questions. Raisy was happy to have someone check her calculations and explained everything enthusiastically. George smiled ever more broadly, but was most pleased to learn that Balthazar's head would be the ideal rocket hull.

``Are you saying I do not even have to set foot outside of the house, and we will fly all the way to the pine trees?''

``We will need to make some transformations,'' Raisy said. ``We have to fill the lower level with brandy.''

``Yes, absolutely. That will not be a problem. Where do you have the fuel now?''

``It is hanging above the main square in barrels,” Philip chimed in. “But we still have to distill it.''

``Let us get to it quickly. I am sure Raisy is sorely missed at home.''

George and Philip headed out to organize the distillation. Raisy stayed in the head of the caterpillar and started the necessary remodeling.

\secbreak

Dewington residents helped Raisy arrange the heavy plates and beams on the day before. They also watched with interest as Mary and the two worms struggled with the clay since the morning. But they had not taken their work entirely seriously, and most did not even know what its goal was. Now more and more fairies stopped in the main square and, looking up at the huge bundle of mead, they asked one another.

``What is in those barrels?''

``I do not know, but it was delivered from up above. From the pasture.''

``It must be honeydew then. But we would not drink so much honeydew in a whole winter...''

``It is not for drinking! They will burn it all in a flying house.''

``Yes, I heard they want to fly to the Moon, because it is eternal winter there.''

``Why do they want to get to the Moon if there is eternal winter there?''

A growing crowd of fairies exchanged such questions and hypotheses on the main square. They nudged each other and fell silent when they saw George arrive. He looked majestic in his purple armor and big white beard. He smiled and waved at Mary, then spoke to the fairies.

``Balthazar, the caterpillar, drank our water, chewed our houses, and poisoned our leaf. Of the palace grounds only a brown stain remains. Today, however, we can be grateful to him because he left behind a real treasure in return. His desiccated head.''

At this point George was surrounded by many a raised eyebrow, but he carried on with the explanation.

``Fall is upon us, and today or tomorrow Dewington too will begin to lose its green color. All the trees turn yellow and red, and all the fairies seek refuge. But there is a distant tree where these days are just like any other. The pines do not care about the winter. The fairies insulate their homes with resin and continue their work until spring. And, thanks to Balthazar, we too will have a place to stay during the coming winter. We are building a rocket out of his head and flying across the valley. We are connecting the two trees with a long line of spider silk, allowing us all to get across. The blue-skinned brothers and sisters living in the pine will welcome our caravans laden with mead and spices, and teach us to build our homes in one of the infinite number of needles.''

The fairies moved closer and their hearts filled with hope. No one was looking forward to the winter. The dark and the cold were the enemy of all life. Waiting for the spring in their tiny shelters was a desperate struggle.

``And what will raise the spirits of our distant relatives the most?'' George continued. ``The brandy! As our luck would have it, Raisy here, was carried all the way from the pine by yesterday's storm. She says aphids do not live on the needles. Thus, the blue fairies rarely taste anything sweet and know not the hearty warmth of spirits. It is a miracle they can survive the winter. So let us cook as much brandy as we can! Let us load up Balthazar's head with the golden liquid! And let us build the bridge between the two trees! The brandy will also serve as propellant for the rocket, but what is left at the end of the trip will be our present to the residents of the pine.''

The drink was a symbol of rare celebrations on Dewington. They did not produce brandy locally, and it was a long way from Solperla. The arrival and supply of merchants was unpredictable. Thus the mention of the drink filled the fairies gathered in the square with enthusiasm. Now they just wanted to know how they could be a part of the plan.

``Philip, the little explorer, has ingeniously delivered the mead, from which the brandy is made, and contrived a process for its distillation. Please follow his instructions. Philip, where do we start?''

Philip had never been so proud, but as much as he straightened his back, he was still only visible from the front row. He climbed onto the bench in the focal point of the drop and started to coordinate the volunteers while standing in the bright light.

As the first step, the children climbed up the threads to the barrels. The adults gathered below them and caught the barrels as they were released. A little girl also released from the tangle a drop of mead bundled in a sheet, but it opened when a volunteer caught it and covered him in the fermented juice. They took more care after that, and passed the bundles down in a chain.

As the cargo dwindled Greg pulled on the threads. Once all the mead had landed he tied them into one knot.

``There is a thick branch a little to the east above Dewington,'' Philip pointed. ``The leaves are warming up in the morning light, but that branch is still in shadow. If the spirits evaporate from the barrels under it, the brandy will condense on the cold bark. Come and help Greg tighten the lines so that Dewington is pulled under the branch!''

Like Philip saw it done on Solperla, they set out to move Dewington by pulling on the web. All the sweat of the strongest fairies was in vain though. They could not shorten the thread enough to allow Greg to anchor it in place. John even let Anaconda help them, but still they were not strong enough.

``The edge of the leaf is under the branch. Would it not be easier to carry the mead there?'' said the accidentally doused volunteer. He was the baker of Dewington, but his usual smell of delicious bread had now been replaced by the stink of mash, and everyone kept a distance from him.

``No point in carrying only the mead, as we could not distill it without the drop,'' Philip explained. ``Which is easier? To transport the drop to the edge of the leaf, or to figure out how to tighten these threads?''

They discussed the matter for a while, but since they had no clear plan for either approach, they could not decide which one was easier. They had to hurry, however, because once the sun warmed the branch, they would have nowhere to collect the fuel. They formed two teams. Philip set out to implement the principle of winches that he had learned on Solperla. Peter, the baker, set out to roll the dewdrop like a bun.

Greg insisted that all lines are equally tense in a good web, but Philip still examined them one by one. He even climbed to the roof of a house so he could pull on the tether, and here he finally felt a bit of give.

``It must have loosened when the shipment was unloaded,'' Greg said. No one blamed him. They were happy to have found a line which they might be able to handle.

A member of their team brought a hair that must have been shed by a caterpillar. It was a smooth, strong rod, about twice as thick as a fairy's finger. If they had managed to twist the thread around it, they could have started winding it and slowly pulling the leaf toward the branch. To loop the silk around the hair, the team wrestled with the thread until Philip fell off the roof.

Anaconda sniffed the sprawled fairy boy. Philip grinned mischievously, grabbed his reins and led him up to the roof. At this point the owner of the house, a pretty young lady, came out to her porch and watched with her hands on her hips.

``I heard you playing on my roof, but I did not expect to see you trying to loop a taut spider's line around a caterpillar's hair with a nematode...''

But that was exactly what was happening, and after a bit more struggle they succeeded at it. They had all worked up a sweat, but after the first twist they did not have to worry anymore that the hair would pop out of the thread. Two fairies could grab the long pole on each end now and push with all their strength to wind the silk thread. Every turn brought Dewington a little closer to the dark arch of the tree branch.

``It is working!'' Philip rejoiced. ``I will let Peter know they do not need to roll the drop.''

The clever baker had not been as lucky as Philip. His team was excitedly running around the dewdrop, trying to figure out how to rescue Peter from it. The poor fairy was floating upside down inside the drop, trying to paddle toward his friends.

``Philip, what are you doing?'' boomed John's deep voice at them. ``That fairy is about to drown! Where is Anaconda?''

``On the roof,'' Philip pointed.

John cast a surprised look, then called the nematode with a long whistle. He held up his hand with a short whistle, then pointed to Peter with a third whistle. Anaconda immediately understood the task. His pointy nose crossed the surface of the drop, as if it had never been there. He was fast on land, but even faster in the water. He reached Peter in the blink  of an eye, coiled around his entire body and took off to leave the drop. His nose easily pierced the surface again, but he got stuck when he tried to pull the fairy out. Fortunately, the fairies were there at once and, taking hold of his bridle, heaved them both through.

Peter spat out a lot of water but was not hurt. He had endless gratitude for Anaconda. Once he recovered fully, he jumped on his feet and fetched some alga scones from the bakery for his rescuer.

\secbreak

Two fairies grabbed a barrel, carried it to the light collected in the focal point of the drop and, as recommended by Alexander, shook it thoroughly. Due to the shaking the mead warmed evenly and started fizzing once it was warm enough. The brown liquid bubbled up and let out an intoxicating smell. Then the foam collapsed and stopped the barrel fizzing. They took it from the sunlight and the next pair of fairies took their place with the next barrel.

Philip and Greg were watching the process from the bottom of the branch above Dewington. Greg's claws were sharp enough to hold on to the surface of the branch, while Philip sat very careful on the edge of a plate of bark, dangling his feet. The shade was quite cold, so Greg had surely regretted that his winter coat was not done yet.

Soon after the fairies started the distillation, the stinging smell reached the branch. Upon contact with the cold surface the spirits condensed and formed tiny globules. Philip was watching eagerly and still did not notice them right away. The dew formed droplets too small for the eye to see. The droplets covered everything and whenever they touched each other they fused into a larger droplet.

``Look, Greg! You are covered in golden beads!''

``So is your hair! There is a little bead at the end of each strand!''

They both swept up the beads and got a radiant orb that just fit in Philip's palm. As he rolled the ball around in his hand, its size grew ever so slightly. At the same time new droplets appeared in his hair. The brandy also collected on the corners of the bark and formed balls of a similar size to the one that Philip held in his hand. When he touched his ball to one growing on an outcropping they merged, and now there was a larger drop trembling on the ledge.

They both enjoyed the game, and soon realized that what they did was also necessary. The small droplets evaporated, the large droplets stayed around. Greg made a small web and, crawling along the bark while his two feet dragged the web, swept up a large golden sphere. Philip popped into the internal cavities of the bark and ousted the pearls that had collected there. They merged the drops into one, and it kept growing with every barrel that the fairies distilled below. When it grew larger than Philip, Greg fastened it with a couple loose threads to be safe. They did not restrict its growth, but made sure that it would only drop down when they were ready.

The boys kept hunting after the beads until the barrels ran out below. ``That was all,'' shouted George from Dewington. ``That was the last barrel. Raisy says the drop looks great!''

Indeed, it was rather large. The unusual smell drew out the inhabitants of the tree. Creatures of all shapes and sizes from the world of the fairies were looking at the golden drop. The rotund form in the shade was about the same size as the sparkling dewdrop in the square of Dewington below. A ring of fairies gazing up surrounded that lower drop. The unusual sight stopped the fairies in the small streets too, and filled them with delight. Someone climbed on the top of their house and watched the drop on the branch above from there.

The bark of the tree also filled with gleaming eyes fixed on the fruit of the hard work. Spiders, mites, tardigrades, caterpillars, larvae, and even adult insects watched curiously. The midges danced excitedly around it, and the hum of their wings filled the air.

``Peter, you can start unwinding,'' Philip called down. ``Head to the second stop!''

The team on the roof of the house, responsible for winding the spider silk, grabbed the rod of hair again. They turned it in the opposite direction this time, but it was still not an easy task. If it slipped out of their hands, the knot would unfold and the leaf break free.

``And here we are,'' said Philip shortly. The drop of fuel was precisely above Balthazar's head.

\secbreak

``Here they are,'' said Mary from the caterpillar's eye. George had built two well-lit reading rooms beneath the enormous eyes. The comfortable couches were now glued to the deck floor with concentrated honeydew. Raisy and George had fixed all the furniture and ornaments in preparation for the flight. Mary had even renamed the rooms. The reading room became the cockpit. The kitchen on the ground floor became the machine room. Raisy was busy installing the nozzle there.

``Just a moment,'' Raisy said. ``Let me check the sealant once more, and then we can load it up.''

They had glued the nozzle in place with honeydew as well. Raisy tapped along the bond and was pleased to find that it had set well. The opening of the nozzle was stuffed with wool from parameciums, and a long wick ran outside from it. Raisy inspected this as well, then climbed up the stairs.

``Come Mary, we better watch this from the outside.''

They scrambled down the hastily constructed stairs from the top floor to the brown swamp of the Stain, retreated from the huge skull, and started jumping and waving.

This was the signal Philip and Greg were waiting for above. To make sure the precious drop would fall straight, they waited until the air stood completely still for a moment, then released the silk tethers from the two sides at once. The drop began to stretch and then separated from the bark. A moment later it flooded the repurposed head of the caterpillar. Thanks to the perfect aim, almost all of the fuel fell into place. It flooded the upper floor through the opening cut into the roof, then streamed down the staircase into the machine room.

Of course Mary and Raisy did not wholly avoid the splashing liquid. They jumped around squealing and shaking the fragrant drops from their hair. Raisy paused, licked her lips and nodded with satisfaction.

Philip and Greg descended between them on a thread, and the time came to say goodbye.

``Lunch is almost done,'' Greg said. ``My mother will ground me if I do not get home in time. Take this thread. Attach it to the rocket, and we will make sure that no matter how far you go it does not snap. Thank you for the game and have a nice journey!''

``Have a nice journey, Philip,'' his mother said. ``It is very nice of you to help Raisy. Enjoy your time on the pine tree, but come home soon!''

``Have a nice journey, Mary,'' her father said. ``You did an amazing job! Learn well from Raisy. Take Babouche with you, he will watch out for you.''

``Have a nice journey, Raisy,'' John said. ``I hope to see you soon and share stories of our latest adventures!''

``Come on, get in!'' George said. ``The fuel has soaked the cotton. We have to get going.''

Before boarding they waved to the fairies gathered around the rocket, then everyone withdrew from the Stain to avoid getting scorched by the fire of the engine. They lit the wick at the edge of the Stain and waited for the take-off hand in hand.

``Ten, nine, eight, seven, six, five, four, three, two, one...''

The fire reached the rocket, and a deep rumbling was heard from Balthazar's head. The sound slowly grew louder, and a blinding light flooded Dewington. Everyone on the leaf took cover, while the travelers inside the head tightened their bonds. With a sudden jerk the rocket took off.

The fire dried the Stain and even charred the center, but did not significantly damage the leaf. The rocket rose ever more rapidly among the branches, and a moment later only a bright pinpoint of light was visible from the leaf. The spider thread they had glued to it had skyrocketed.

``We are flying!'' they cheered in Balthazar's head.

``The trajectory is good too. We only need to turn three degrees to the left,'' Raisy said as she excitedly compared measurements and calculations. George pulled on a handle that turned the nozzle to a slightly different orientation.

Philip and Mary watched the scenery unfolding below them from the flight deck.

\begin{center}
The End
\end{center}%

\end{document}  

